% ================================ Lecture 6 ===================================
\flashcard{\normalfont
  A \blank{\textbf{digital signature}} associates a mark unique to an individual with a body of text (e.g. Only A can sign a message, since only A has access to the private key. Anyone can verify A’s signature, since everyone has access to its public key).
}

\card{\normalfont
  What are the requirements of a \textbf{digital signature}?
}{\normalfont
  \begin{flushleft}
    - \textbf{Message dependent}: Non Reusable and Ensures integrity \\
    - \textbf{Signer dependent}: Unforgeable and Ensures authenticity \\
    - \textbf{Verifiable}: others should be able to verify that the signature is indeed from the originator.
    Both integrity and authenticity are necessary to ensure \textbf{non-repudiation}, i.e. the signer can not falsely deny that they have generated the signature.
  \end{flushleft}
  Digital Signature Requirements
}

\card{\normalfont
  What does a \textbf{digital signature} scheme consist of?
}{\normalfont
  \begin{flushleft}
    - A key generation algorithm \\
    - A signature (generation) algorithm \\
    - A signature verification algorithm
  \end{flushleft}
  Digital Signature Scheme Components
}

\card{\normalfont
  Which are the two well known \textbf{digital signature} schemes?
}{\normalfont
  \begin{flushleft}
    - \textbf{RSA} encryption algorithm can be used in reverse to produce a signature. \\
    - \textbf{DSA} is a signature algorithm based on discrete logarithms.
  \end{flushleft}
  Digital Signature Schemes
}

\card{\normalfont
  What are the \textbf{differences} between the \textbf{RSA} algorithm and the \textbf{DSA} algorithm?
}{\normalfont \footnotesize
  \begin{flushleft}
    - Security is based on RSA: difficulty of factoring large number and DSA: difficulty of taking discrete logarithms  \\
    - RSA Can encrypt and sign while DSA can only sign messages \\
    - RSA is faster than DSA in signature verification, and about the same in signature generation. In DSA some signature computation can be computed a priori \\
    - RSA can recover the message digest from the signature, while DSA can not. \\
    - DSA: need to choose a unique secret number k for each message
  \end{flushleft}
  RSA vs DSA
}
