% ================================ Lecture 1 ===================================

\card{ \normalfont
  What does \textbf{network security} consist of?
}{ \normalfont
 \begin{flushleft}
   - Security problems and countermeasures in the transmission of information. \\
   - Security problems and countermeasures in networked computer systems.
 \end{flushleft}
 Network Security
}

\card{ \normalfont
  What are some examples of \textbf{security threats}?
}{ \normalfont
  \begin{flushleft}
    - Disclosure \\
    - Deception \\
    - Disruption \\
    - Attacks via Malware \\
    - Hacking as a Service \\
  \end{flushleft}
  Security Threats
}

\flashcard{ \normalfont
  \blank{\textbf{Disclosure}} is the release of message contents to any person or process not possessing the appropriate cryptographic key (e.g. \blank{snooping}, \blank{sniffing}).
}

\card{\normalfont
  What is meant by \textbf{non repudiation}?
}{\normalfont
  \textbf{Non repudiation} means that the signer can not falsely deny that they have generated the signature.
}

\flashcard{ \normalfont
  \blank{\textbf{Deception}} examples include:
  \begin{flushleft}
    - Interception \\
    - Modification \\
    - Spoofing \\
    - Repudiation of origin \\
    - Denial of receipt \\
  \end{flushleft}
  Security Threats
}

\flashcard{ \normalfont
  \blank{\textbf{Disruption}} examples include:
  \begin{flushleft}
    - Modification \\
    - Delay \\
    - Denial of Service (DoS) \\
  \end{flushleft}
  Security Threats
}

\card{ \normalfont
  What are some examples of \textbf{malware types} from Attacks Via Malware?
}{ \normalfont
  \begin{flushleft}
    - Worms
    - Viruses
    - Trojan
  \end{flushleft}
  Malware Types
}

\card{ \normalfont
  What are some \textbf{security problems and challenges}?
}{\normalfont \small
  \begin{flushleft}
    - Naive users: lack of security awareness \\
    - Inadequate management procedures \\
        - Insecure system set-up and configuration \\
        - Lack of proper policy making, implementation and enforcement procedures \\
    - Global networks without national boundaries \\
    - Heterogeneous devices, e.g. laptops, iPhones and PDAs, with universal connections \\
    - Wireless and open channels \\
    - Anonymous nature of many internet based services \\
  \end{flushleft}
  Security Problems and Challenges
}

\flashcard{ \normalfont
  Securing information through CIA: \\
  \begin{flushleft}
    - \blank{\textbf{Confidentiality}}: keeping data and resources hidden \\
    - \blank{\textbf{Integrity}}: data \blank{integrity} (making sure data is authentic) and origin \blank{integrity} (authentication) \\
    - \blank{\textbf{Availability}}: ensuring data/service is available to authorised users.
  \end{flushleft}
  CIA
}

\card{ \normalfont
  What is the \textbf{life cycle} of \textbf{achieving security}?
}{ \normalfont \small
  \begin{flushleft}
    - Threats analysis and identification: decide \textbf{what to protect} \\
    - Policy specification (defining security goals): define \textbf{what is, and is not, allowed} \\
    - Design and implementation (enforcing policies to achieve security goal): decide \textbf{how to protect} in order to \textbf{satisfy the specification} with technical and procedural measures \\
    - Operation and maintenance (security assurance): assess \textbf{how well} the implementation has \textbf{achieved} its security \textbf{goal}
  \end{flushleft}
  Life Cycle of Achieving Security
}

\flashcard{ \normalfont
  An \blank{\textbf{Attack Tree (Threat Tree)}} is a conceptual diagram showing how an asset, or target, might be attacked.
}

\card{ \normalfont
  What does an \textbf{Attack Tree} consists of?
}{ \normalfont
  \begin{flushleft}
    - root node: the attack goal \\
    - children nodes: conditions which must be satisfied to make the direct parent node true \\
    - leaf nodes
  \end{flushleft}
  Attack Tree
}

\card{ \normalfont
  What are the two conditions in an Attack Tree?
}{\normalfont
  \begin{flushleft}
    - OR: represents alternative attack methods or avenues in the attack \\
    - AND: represents multiple steps in launching an attack
  \end{flushleft}
  Attack Tree Conditions
}

\flashcard{ \normalfont
  Each node may be given a value to indicate, e.g: \\
  \begin{flushleft}
    - \blank{Likelihood} that an attacker will mount the attack, or \blank{probability} of succeeding the attack \\
    - \blank{Cost} in succeeding the attack, in terms of monetary cost, or time taken to accomplish the attack, etc. \\
  \end{flushleft}
  Like this you could identify and make a decision as what, where and how to protect your asset.
}

\flashcard{ \normalfont
  \blank{\textbf{Security measures}} are a method, protocol, tool or procedure used to address the risks identified (or to enforce a security policy).
}

\flashcard{ \normalfont
  \blank{Prevention} is a security measure which:
  \begin{flushleft}
    - Block attacks by closing vulnerabilities \\
    - Reduce the level of risks by making attacks harder \\
    - Make another target more attractive than this one \\
    - E.g. access control (firewalls), encryption, digital signatures
  \end{flushleft}
  Security Measures
}

\flashcard{ \normalfont
  \blank{Detection} is a security measure which measures taken during or after the attacks, e.g. auditing and intrusion \blank{\textbf{detection}}.
}

\flashcard{\normalfont
  \blank{\textbf{Recovery}} is a security measure which stops attacks, asses and repairs damage. It continues t function correctly even if the attacks succeed.
}

\flashcard{\normalfont
  A security measure consists of \blank{\textbf{accepting}} the attack and doing \blank{\textbf{nothing}}.
}

\flashcard{ \normalfont
  A \blank{\textbf{communication}} security model: emphasis is on protecting data while in transit.
}

\flashcard{\normalfont
  A \blank{\textbf{network}} security model: focus is on protecting data and services on a \blank{\textbf{network}} against external attacks or unauthorised usage. It has multi-level security measures, however, the use of mobile devices will make the boundary hard to define.
}

\flashcard{\normalfont
  An \blank{\textbf{e-commerce}} security model: the opponent is a misbehaving insider. The third party is now a trusted third party TTP, e.g an arbitrator, that offers some services. Non-repudiation services generate the evidence the arbitrator will consider when resolving a dispute.
}


% ================================ Lecture 2 ===================================
\flashcard{ \normalfont
  \blank{\textbf{Cryptography}} is \textit{the art of keeping messages secure}. (Schneier)
}

\card{ \normalfont
  What are some of the uses of \textbf{cryptography}?
}{ \normalfont \footnotesize
  \begin{flushleft}
    - Confidentiality (secrecy, privacy) of data in transmission and in storage \\
    - Integrity of data in transmission and in storage \\
    - Origin authentication of data \\
    - Authentication of identity \\
    - Credentialing systems (a proof of qualifications or competence of a person) \\
    - Digital signatures \\
    - Electronic money \\
    - Threshold cryptosystems \\
    - Secure multi-party communications \\
    - Digital right management \\
    - Electronic voting, etc.\\
  \end{flushleft}
  Cryptography Uses
}

\flashcard{ \normalfont
  \blank{\textbf{Encryption}} can be used to achieve secure communications over an insecure channel.
}

\flashcard{ \normalfont
  \blank{\textbf{Symmetric}} key based encryption uses conventional ciphers. The same key is used for encryption and decryption (e.g. historical ciphers, modern ciphers).
}

\flashcard{\normalfont
  \blank{\textbf{Asymmetric}} key based encryption uses public key ciphers. Different keys are used for encryption and decryption (e.g. modern ciphers).
}

\flashcard{\normalfont
  \blank{\textbf{Plaintext}} or \blank{\textbf{cleartext}} is a message in its original form.
}

\flashcard{\normalfont
  \blank{\textbf{Ciphertext}} is a message in an encrypted form.
}

\flashcard{\normalfont
  \blank{\textbf{Encryption}} is coding a message to hide its meaning, while \blank{\textbf{decryption}} is converting an \blank{\textbf{encrypted}} message back to its original form.
}

\flashcard{\normalfont
  \blank{\textbf{Cipher}} or \blank{\textbf{Cryptosystem}} is the system that performs encryption and decryption.
}

\flashcard{\normalfont
  An \blank{\textbf{unconditional security}} is the system that cannot be defeated, no matter how much power is available by the adversary.
}

\flashcard{\normalfont
  \blank{\textbf{Computational security}} is the perceived level of computation required to defeat the system using th best known attack exceeds, by a comfortable margin, the computational resources of the hypothesized adversary (e.g. given limited computing resources, it takes very long time to break a cipher).
}

\flashcard{\normalfont
  A \blank{\textbf{provable}} security means that the difficulty of defeating the system can be shown to be essentially as difficult as solving a well-known and supposedly difficult problem (e.g. integer factorisation).
}

\flashcard{\normalfont
  \blank{\textbf{Ad hoc}} security are claims of security which generally remain questionable, where unforseen attacks remain a threat.
}

\card{\normalfont
  What are the two classical ciphers?
}{\normalfont
  \begin{flushleft}
    1. Substitution ciphers: monoalphabetic and polyalphabetic. \\
    2. Transportation ciphers.
  \end{flushleft}
  Classical Ciphers
}

\card{\normalfont
  What are the encryption techniques?
}{\normalfont
  \begin{flushleft}
    - Classical (historical) algorithms are based on substitution (based on confusion, e.g. a becomes b) and permutation/transposition (based on diffusion, e.g. abcd becomes dacb) \\
    - XOR operator \\
    - Simple non-secure ciphers: Shift cipher - caesar cipher; Vigenere Cipher, etc. \\
    - Secure cipher: One-time pad
  \end{flushleft}
  Encryption Techniques
}

\flashcard{\normalfont \small
  \blank{\textbf{Ceaser Cipher}} or shift cipher uses simple substitution: each letter is translated to the letter a fixed number of letters after it in the alphabet. The operation could be expressed using addition modulo 26:
  \begin{flushleft}
    - The message must be a sequence of letters, each letter is identified with a number \\
    - The key k is a number in the range 1 to 25 \\
    - Encryption/decryption involves +- k to each letter (mod 26) \\
  \end{flushleft}
  Shift Cipher
}

\flashcard{\normalfont
  \blank{\textbf{Brute force attack}} or exhaustive key search tries all possible keys.
 }

 \card{\normalfont
   What are the three characteristics that make the Brute force attack practical?
 }{\normalfont
  \begin{flushleft}
    - The encryption and decryption algorithms are in public domain \\
    - There are only 25 keys to try out \\
    - The language of the plaintext is easily recognisable (e.g. compressed text not) \\
  \end{flushleft}
  Brute force attack practical reasons
}

\flashcard{\normalfont
  The \blank{\textbf{one-time pad}} is a special variant of the stream cipher and it is truly a perfect cipher: it uses a one-time random key that is as long as the plaintext with no repetitions (only used once). If used properly, it is provably unbreakable.
}

\card{\normalfont
  What are some of the \textbf{problems} of the \textbf{one-time pad}?
}{\normalfont
  \begin{flushleft}
    - No way to remember the entirety of the random key string. \\
    - It’s too expensive for most applications as it consumes as much key material as there is traffic. \\
    - Key management is hard as the need for non-repeating keys has a problem with storing and distributing them. \\
    - Absolute synchronisation between sender and receiver is really hard to achieve.\\
  \end{flushleft}
  Problems with the one-time pad
}

\card{\normalfont
  What is the main idea of a \textbf{stream cipher}?
}{\normalfont
  To replace the random key in one-time pad by a pseudo-random sequence, generated by a cryptographic pseudo-random generator that is seeded with the key. \\
  \textit{Ciphertext = plaintext XOR keystream} \\
  This is a dangerous security property and we must never reuse the same keystream to encrypt two different messages.
}

\flashcard{\normalfont
  The \blank{\textbf{transportation (permutation)}} texhnique performs a permutation on the plaintext.
}

\card{\normalfont
  What are some common types of \textbf{attacks}?
}{\normalfont
  \begin{flushleft}
    - Try to break or crack the algorithm by exploring any flaws in it e.g. frequency analysis. \\
    - Assume attacker recognises plaintext, try to decrypt ciphertext with every possible key until…, e.g. brute force attack (Also exhaustive key search attack) \\
    - Run the algorithm on massive amounts of plaintext and find the one plaintext that encrypts to the ciphertext that it’s being analysed, e.g. dictionary attack.\\
  \end{flushleft}
  Common types of attacks
}

\card{\normalfont
  Ciphertest-only attacks? (e.g. frequency attcks)
}{\normalfont
  \begin{flushleft}
    - Attacker knows ciphertexts of several messages encrypted with the same key, plaintext is recognisable. \\
    - The goal is to find the plaintext, possibly the key \\
  \end{flushleft}
  Ciphertext-only attacks
}

\card{\normalfont
  Known-plaintext attack? (e.g. dictionary attack)
}{\normalfont
  \begin{flushleft}
    - Attacker observes <plaintext, ciphertext> pairs encrypted with the same key. \\
    - The goal is to find the key. \\
  \end{flushleft}
  Known-plaintext attack
}

\card{\normalfont
  Chosen-plaintext attack?
}{\normalfont
  \begin{flushleft}
    - Attacker can choose the plaintext and look at the paired ciphertext. \\
    - The goal is to find the key. \\
  \end{flushleft}
  Chosen-plaintext attack
}

\flashcard{\normalfont
  \blank{\textbf{Cryptanalysis attacks}} often exploit the redundancy of natural language: lossless compression before encryption removes redundancy.
}


% ================================ Lecture 3 ===================================
\flashcard{\normalfont
  In a \blank{\textbf{block}} cipher, the plaintext is divided into \blank{blocks} of fixed length which are encrypted one at a time.
}

\card{\normalfont
  What is the \textbf{design criteria} of \textbf{block ciphers}?
}{\normalfont \small
  \begin{flushleft}
    - \textbf{Completeness}: each bit of the output should depend on every bit of the input and every bit of the key. \\
    - \textbf{Avalanche effect (Diffusion)}: changing one bit in the input should change many bits in the output. Also, changing one key bit should result in the change of many bits in the output.\\
    - \textbf{Statistical independence (Confusion)}: input and output should appear to be statistically independent.
    A complex encryption function can be built out of some simple operations (round function) by repeatedly using them.
  \end{flushleft}
  Design Criteria of Block Ciphers
}

\flashcard{\normalfont
  \blank{\textbf{Feistel block cipher}} is an example implementation of a block cipher. There is an initial permutation of bits which is then split in left and right halves. 16 rounds of identical operations, but each round uses a different subkey. Inverse initial permutation.
}

\flashcard{\normalfont
  Ciphers that use substitution and permutation are called \blank{\textbf{substitution-permutation (S-P) networks}}. They can be efficiently implemented on both hardware and software platforms.
}

\flashcard{\normalfont
  The \blank{\textbf{Data encryption Standard (DES)}} was first published in 1977 as a US Federal standard. IT is a de facto international standard for banking security. It’s a Feistel block cipher - block length is 64 bits, key K is 56 bits. The subkeys k1, k2… k16 are each 48 bits, generated from key K. \\
  The DES decryption algorithm is the same as the encryption one; the only difference is that the keys for each round must be used in reverse order, i.e k16 first and k1 last.
}

\card{\normalfont
  What is the architecture of \textbf{each round} of a \textbf{DES}?
}{\normalfont
  Li = Ri+1 and Ri - Li-1 xor f(Ri-1, Ki)
}

\card{\normalfont
  What are the steps of a \textbf{round function} of a \textbf{DES}?
}{\normalfont \small
  \begin{flushleft}
    1. \textbf{Expansion permutation}: Right half (32 bits) is expanded (and permuted) to 48 bits. Diffuses relationship of input bits to output bits. \\
    2. \textbf{Use of Round Key}: 48 bits are XOR-ed with the round key (48 bits). \\
    3. \textbf{Splitting}: result is split into eight lots of six bits each.\\
    4. \textbf{S-Box} (S = Substitution): each six bit lot is used as an index to an S-box to produce a four bit result.
    5. \textbf{P-Box} (P = Permutation): 32 bits output from 8 S-Boxes are permuted = the output of f.
  \end{flushleft}
  DES round function steps
}

\card{\normalfont
  What is the operation of an \textbf{S-Box}?
}{\normalfont
  \begin{flushleft}
    - Each of the 8 different S-boxes is a table of 4 rows and 16 columns \\
    - The 6 input bits specify which row and column, i.e. cell, to use. Bits 1 and 6 select the row, while bits 2-5 select the column.
    - The decimal value in the cell is then converted into a 4-bit result, which is the output from the S-box
  \end{flushleft}
  S-Box Operation
}

\card{\normalfont
  What is the \textbf{weakness} of an \textbf{S-Box}?
}{\normalfont
  \begin{flushleft}
    The 56-bit key which is good enough to deter casual DES key browsing, but not for a dedicated adversary. \\
    Use of a 56-bit key can be broken on average in 255 (i.e. 3.6 * 1016) trials. \\
    - A DES chip does 1 million encryptions per second.\\
    - A million chips in parallel do 1012 trials per second. \\
    For today’s computing power, the key size should be at least 128 bits. Improvements: Triple DES (3DES), AES (Rijndael).
  \end{flushleft}
  S-Box weakness
}

\flashcard{\normalfont
  \blank{\textbf{Triple DES}} involves use of \blank{two} or \blank{three} DES keys.
}

\card{\normalfont
  What are the \textbf{two types} of \textbf{Triple DES}?
}{\normalfont
  \begin{flushleft}
    1. EDE2 (triple DES using 2 keys): It uses 2 DES keys (K1, K2), encryption algorithm Em and decryption algorithm D, i.e. C = EK1(Dk2(EK1(M))). So the key length is 112 bits. The use of D here does not have any security implication; it just makes triple DEs backward competitive with single DES if K1 = K2.\\
    2. EDE3 (triple DES using three keys): It uses three keys, so C = EK3(Dk2(EK1(M))). The key length is 168 bits.
  \end{flushleft}
  Types of Triple DES
}

\card{\normalfont
  How does the \textbf{meet-in-the-middle attack} work?
}{\normalfont
  \begin{flushleft}
    A table of keys is built and f(k, M) computed for every possible key, where f is an encryption function, and M is a known message. Eavesdrop a value f(k’, M) and if it’s the same as f(k, M) then there is a good chance k’ = k.
  \end{flushleft}
  Meet-in-the-middle Attack
}

\card{\normalfont
  Why did NIST call for \textbf{algorithms} to \textbf{replace DES}?
}{\normalfont
  Because algorithm and implementation characteristics are fast and have low resource consumption. \\
  Cost: fast in both hardware and software.
}

\card{\normalfont
  What was the officially nominated \textbf{Advanced Encryption Standard (AES)} in 2001?
}{\normalfont
  Vincent Rijmen and Joan Daemen’s algorithm, Rijndael.
}

\flashcard{\normalfont
  \textbf{DES} and \textbf{AES} are both a \blank{\textbf{symmetric block}} cipher.
}

\card{\normalfont
  What does a \textbf{symmetric block cipher} entail?
}{\normalfont \footnotesize
  \begin{flushleft}
    - The same key is used to encrypt and decrypt the message. \\
    - The plaintext and the ciphertext have the same size. \\
    - Block size is 128 bits (others are allowed but not recognised by the standard). \\
    - The key lengths are 128 192, or 256 bits, i.e. the standard comprises three block ciphers: AES-128, AES-192 and AES-256. \\
    - It is a substitution-permutation cipher involving r rounds: For key length 128, r = 10; For key length 193, r = 12; For key length 256, r = 14.
  \end{flushleft}
  Symmetric block cipher properties
}

\card{\normalfont
  What does the \textbf{round transformation} consist of?
}{\normalfont
  \begin{flushleft}
    - Byte substitution. \\
    - Shift rows. \\
    - Mix columns. \\
    - Round key addition.
  \end{flushleft}
  Round Transformation Elements
}

\card{\normalfont
  What are some properties of the \textbf{AES}?
}{\normalfont
  AES has a sequential and light-weight key schedule. \\
  AES has a fixed block size of 128  bits (16 bytes) called a state.
}

\card{\normalfont
  How does the \textbf{substitute bytes} of an AES work?
}{\normalfont \small
  \begin{flushleft}
    - This SubBytes transformation is a simple table lookup. \\
    - Only one S-Box for the whole cipher, a 16 x 16 matrix of byte values, that contains a permutation of all possible 256 8-bit values. \\
    - Each individual byte of state is mapped into a new byte in this way: leftmost 4 bits of the byte are used as a row value; rightmost 4 bits used as a column value. \\
    - These row and column values serve as indexes into the S-box to select a unique 8-bit output value.
  \end{flushleft}
  AES Substitute Bytes
}

\card{\normalfont
  How does the \textbf{ShiftRows} transformation of an AES work?
}{\normalfont
  \begin{flushleft}
    - 1st row: not altered; \\
    - 2nd row: a 1-byte circular left shift; \\
    - 3rd row: a 2-byte circular left shift; \\
    - 4th row: a 3-byte circular left shift. \\
    Decryption uses shift to the right. \\
    This step permutes between the columns.
  \end{flushleft}
  AES ShiftRows
}

\card{\normalfont
  How does the \textbf{MixColumns} transformation of an AES work?
}{\normalfont
  The \textbf{MixColumns} transformation operates on each column individually. Each byte of a column is mapped into a new value hat is a function of all four bytes in the column; the transformation is performed in GF(28). \\
  This with \textbf{ShiftRows} transformation provides \textbf{diffusion}.
}

\card{\normalfont
  How does the \textbf{AddRoundKey} transformation of an AES work?
}{\normalfont
  In the \textbf{AddRoundKey} transformation, each byte of the state is combined with the round key using XOR, i.e. the 128 bits of state are bitwise XORed with the 128 bits of the round key (the round key is derived from the cipher key using a key schedule).
}

\card{\normalfont
  What is the pseudo-code for \textbf{AddRoundKey} for \textbf{AES-128 Encryption}?
}{\normalfont
  \begin{flushleft}
    \textbf{AddRoundKey(S, K[0]);} K[0] is the cipher key, K, and other round keys are expanded from K. \\
    for(i = 1; i<=9; i++)
    \begin{center}
      SubBytes(S); \\
      ShiftRows(S); \\
      MixColumns(S); \\
      AddROundKeys(S, K[i]);
    \end{center}
    SubBytes(S); \\
    ShiftRows(S); \\
    AddRoundKey(S, K[10]);
  \end{flushleft}
  AddRoundKey AES-128 Encryption Pseudo-code
}

\card{\normalfont
  What is the pseudo-code for \textbf{AddRoundKey} for \textbf{AES-128 Decryption}?
}{\normalfont
  \begin{flushleft}
    (first apply InvMixColumns to the round key) \\
    AddRoundKey(S, K[10]); \\
    for(i = 9; i>=1; i++) \\
    \begin{center}
      InvSubBytes(S); \\
      InvShiftRows(S); \\
      InvMixColumns(S); \\
      AddRoundKey(S, K[i]);
    \end{center}
    InvSubBytes(S); \\
    InvShiftRows(S); \\
    AddRoundKeys(S, K[0]);
  \end{flushleft}
  AddRoundKey AES-128 Decryption Pseudo-Code
}

\card{\normalfont
  What are the properties of a \textbf{DES}?
}{\normalfont
  \begin{flushleft}
    - Substitution-Permutation, iterated cipher, Feistel structure. \\
    - 64-bit block size, 56-bit key size. \\
    - 8 different S-boxes. \\
    - design optimised for hardware implementations. \\
    - closed (secret) design process.
  \end{flushleft}
  Data Encryption Standard (DES)
}

\card{\normalfont
  What are the properties of an \textbf{AES}?
}{\normalfont
  \begin{flushleft}
    - Substitution-Permutation, iterated cipher. \\
    - 128-bit block size, 128-bit (192 or 256) key size. \\
    - 1 S-Box. \\
    - Design optimised for byte-oriented implementations. \\
    - Open design and evaluation process.
  \end{flushleft}
  Advanced Encryption Standard (AES)
}

\card{\normalfont
  What are the three \textbf{modes of operation} when encrypting large messages?
}{\normalfont
  \begin{flushleft}
    - ECB - Electronic Code Book \\
    - CBC - Cipher Book Chaining \\
    - CTR - Counter mode \\
  \end{flushleft}
  These modes of operation have been standardised internationally and are applicable to any block ciphers.
}

\card{\normalfont
  What are the properties of an \textbf{ECB mode} encryption?
}{\normalfont \footnotesize
  \begin{flushleft}
    - Block are encrypted independently of other blocks. Reordering ciphertext blocks result in correspondingly reordered plaintext blocks. Ciphertext blocks can be cut from one message and pasted in another, so block replay or block insertion (or deletion) attacks may go undetected.\\
    - The same block of plaintext always produces the same ciphertext (with the same key): Patterns in plaintext show up in ciphertext. \\
    - Error propagation: one bit error in a ciphertext block affects only the corresponding plaintext block. \\
    - Not recommended for messages longer than one block, or if keys are reused for more than one block.
  \end{flushleft}
  ECB mode
}

\card{\normalfont
  What are the properties of a \textbf{CBC mode} encryption?
}{\normalfont \footnotesize
  \begin{flushleft}
    - Plaintext is divided into blocks and the last block is padded if necessary. \\
    - Cn = Ek(Mn xor Cn-1) where C0 = IV (initialisation vector)\\
    - In this example, the plaintext is M1M2, and the ciphertext is C0C1C2.\\
    - Ciphertext blocks Cj depends on Mj and all preceding plaintext blocks. Any repeated patterns in the plaintext are concealed by the feedback. \\
    - Using different IVs in different encryption operations will result in the same plaintext producing different ciphertexts.
  \end{flushleft}
  CBC mode
}

\card{\normalfont
  What are the properties of a \textbf{CTR mode} encryption?
}{\normalfont \footnotesize
  \begin{flushleft}
    - Uses a counter, equal to the plaintext block size. Its value must be different for each plaintext block. Typically the counter is initialised to some value, and then incremented by 1 for each subsequent block (modulo 2n, where n is the block length). \\
    - Each block can be decrypted independently of the others: Parallelizable, Support random access, The values to be XORed with the plaintext can be precomputed \\
    - The counter needs to be synchronised: If a block is inserted into or deleted from the ciphertext stream then synchronisation is lost and the plaintext cannot be recovered \\
    - No error propagation: A ciphertext block that is modified during transmission affects only the decryption of that block.
  \end{flushleft}
  CTR mode
}

\card{\normalfont
  What are the differences between a \textbf{block cipher} and a \textbf{stream cipher}?
}{\normalfont \footnotesize
  \begin{flushleft}
    While block ciphers encrypt block of characters, stream ciphers encrypt individual characters or bit streams. \\
    Stream ciphers:\\
    - Are usually faster than block ciphers in hardware; mostly used for continuous communications and/or real time applications. \\
    - Requires less memory space, so cheaper for resource restrained devices such as embedded sensors. \\
    - Have limited or no error propagation, so advantageous when transmission errors are probable. \\
    - Can be built out of block ciphers, e.g. by using CRT modes.
  \end{flushleft}
  Block Ciphers vs Stream Ciphers
}


% ================================ Lecture 4 ===================================
\flashcard{\normalfont
  \textbf{Conventional/ symmetric} cryptography is based on \blank{\textbf{shared secret keys}}.
}

\card{\normalfont
  What are the problems with \textbf{symmetric/ conventional cryptography}?
}{\normalfont
  \begin{flushleft}
    A separate key is needed for each pair of users (or even for each ciphertext encryption -> session key) \\
    - So an n-user system requires n*(n-1)/2 keys -> the n2 problem. \\
    - Generating and distributing these keys are a challenging problem. \\
    - Maintaining security for the keys already distributed is also challenging: can one remember so many keys? \\
    As two parties share the same key, non-repudiation can not be achieved.
  \end{flushleft}
  Problems with symmetric/ conventional cryptography
}

\flashcard{\normalfont
  \blank{\textbf{Public key}} cryptosystems are based on mathematically hard problems rather than substitution/ transportation (permutation) ciphers.
}

\card{\normalfont
  How does \textbf{public-key} cryptography work?
}{\normalfont
  \begin{flushleft}
    A pair of keys is used: One is private (secret), the other can be made public. The pair of private and public keys are related mathematically. It is infeasible to generate one from the other. \\
  Encryption generated with one key can only be decrypted with the other key in the pair.
  \end{flushleft}
  Public-key cryptography
}

\flashcard{\normalfont
  \blank{\textbf{Confidentiality}} protection is only applied to short messages, e.g. for secure transportation of symmetrical keys. \\
  It is achieved by encrypting the plaintext M using the recipient's public key. Only the recipient has the corresponding private key so M can only be read by the recipient.
}

\flashcard{\normalfont
  A \blank{\textbf{signature}} is put on the hash value of M, and a \blank{\textbf{timestamp}} should also be included. This is used for message authentication and integrity and non repudiation of message origin. \\
  It it achieved by \blank{signing} M (actually the hash of it) using the sender's \textbf{private key}. Only the seder has the private key, so the message must have been signed by the sender.
}

\flashcard{\normalfont
  \blank{\textbf{Public key cryptography}} is based on the idea of a \textit{trapdoor} function, or mathematically hard problems.
}

\card{\normalfont
  Why is PKC using mathematically hard problems?
}{\normalfont
  \begin{flushleft}
    - Easy to generate keys (public and private) \\
    - Easy to encrypt and decrypt if the right key is known. \\
    - Hard to compute private key from public key. \\
    - Hard to recover plaintext from ciphertext without the right key.
  \end{flushleft}
  Reasons for using mathematically hard problems for PKC
}

\card{\normalfont
  What is the mathematical definition of \textbf{modulo}?
}{\normalfont
  \textit{a = b mod n}, which means there exists an integer number k such that a can be represented as a = k *n + b with the condition that 0 <= b <= n-1. \\
  Given integers a, b, and n != 0, a is congruent to b modulo n, if and only if a - b = k * n for some integer k, i.e. n divided (a-b). The notation is a = b (mod n). We call n the \textbf{modulus}, and b is \textbf{remainder} or \textbf{residue} of a modulo n.
}

\card{\normalfont
  What does the \textbf{RSA algorithm} consist of?
}{\normalfont
  \begin{flushleft}
    The algorithm consists of two numbers, the modulus (represented by the letter n) and the public exponent (represented by the letter e). \\
    The modulus is the product of two very large prime numbers (100 to 400 digits), represented by letters p and q (they need to be kept secret). \\
    It is a block cipher in which the plaintext and ciphertext are integers between 0 and n-1 for some n.
  \end{flushleft}
  RSA Algorithm
}

\card{\normalfont
  What are the three stepts of the \textbf{RSA algorithm}?
}{\normalfont
  \begin{flushleft}
    1. Key generation \\
    2. Encryption \\
    3. Decryption
  \end{flushleft}
  RSA Algorithm Steps
}

\card{\normalfont
  What is the pseudo-code for the \textbf{key generation} step of the \textbf{RSA algorithm}?
}{\normalfont \footnotesize
  \begin{flushleft}
    - Select two large primes (e.g. 200 digits) p and q \\
    - Calculate n = p * q and phi(n) = (p-1) * (q-1) \\
    - Select integer e relatively prime to phi(n) and 1 < e < phi(n) \\
    - Calculate d = e (to -1) mod phi(n) (or de = 1 mod phi(n)) \\
    - \textbf{Public key = {e, n}} \\
    - \textbf{Private key = {d, n}} \\
    - So: p and q are private and chosen; n= p * q is public and calculated (but keep p and q secret); e is public and chosen, and d is private and calculated.
  \end{flushleft}
  RSA Key Generation Step Pseudo Code
}

\card{\normalfont
  What is the pseudo-code for the \textbf{encryption} step of the \textbf{RSA algorithm}?
}{\normalfont
  \begin{flushleft}
    - Represent the plaintext as an integer M in [0, n-1], i.e. M < n \\
    - Ciphertext: C = M (to e) mod n
  \end{flushleft}
  RSA Encryption Step Pseudo Code
}

\card{\normalfont
  What is the pseudo-code for the \textbf{decryption} step of the \textbf{RSA algorithm}?
}{\normalfont
  \begin{flushleft}
    - Ciphertext is C \\
    - Plaintext is M = C (to d) mod n
  \end{flushleft}
  RSA Decryption Step Pseudo Code
}

\card{\normalfont
  What does the \textbf{security} of the \textbf{RSA algorithm} rely on?
}{\normalfont \small
  \begin{flushleft}
    - The security of the RSA relies on the difficulty of finding d given {e, n}. The problem of computing d from {e, n} is computationally equivalent to the problem of factoring n: if one can factorise n, then he can find p and q, and hence calculate d. \\
    - p and q should differ in length by only a few digits, and both should be on the order of 100-200 digits or even larger. n with 150 digits could be factored in about 1 year. Factoring n with 200 digits could take about 1000 years (assuming about 1012 operations per second).
  \end{flushleft}
  RSA Security
}

\flashcard{\normalfont
  The \blank{\textbf{hybrid cryptosystem}} was introduces because the \blank{\textbf{symmetric ciphers}} have key management problems and can not provide non repudiation services without the involvement of a trusted third party.
}

\flashcard{\normalfont
  \textbf{Hybrid cryptosystems} are the combination of \blank{\textbf{public key ciphers}} and \blank{\textbf{symmetric ciphers}}.
}

\card{\normalfont
  What does a \textbf{hybrid cryptosystem} contain?
}{\normalfont
  A \textbf{hybrid cryptosystem} contains a public cipher for symmetric key establishment/transportation and/or for digital signature generation and a symmetric cipher for bulk encryption.
}

\card{\normalfont
  \textbf{Hybrid cryptosystems} are used to speed thing up. This process is called \textbf{digital enveloping}. What does it entail?
}{\normalfont
  \begin{flushleft}
    - A symmetrical algorithm with a random session key (bulk encryption key) is used to encrypt the message; \\
    - A public-key algorithm is used to encrypt the random session (symmetric) key.
  \end{flushleft}
  Digital Enveloping
}

\card{\normalfont
  What are the two primary uses of \textbf{public key cryptography}?
}{\normalfont \footnotesize
  \begin{flushleft}
    1. Key establishment \\
    \begin{flushleft}
      - Key exchange (or key transportation): a generates asymmetric key and transports it to b using b’s public key. RSA can be used for key exchange. \\
      - Key agreement: Both a and b co-operate to generate a shared key.
DH is a key agreement algorithm. \\
    \end{flushleft}
    2. Digital signatures: often using RSA or DSS (Digital Signature Standard) \\
  \end{flushleft}
  Public key cryptography provides capabilities that can not be attained with symmetric cryptography, but it is too inefficient to be used alone for large text encryption.
}


% ================================ Lecture 5 ===================================
\card{\normalfont
  What is the \textbf{cryptographic checksum} used for/ protecting?
}{\normalfont
  \begin{flushleft}
    - Content authentication (origin + integrity) for any kind of message including unstructured. \\
    - Non-repudiation of orogin (digital signature) \\
    - Anti-replay (i.e achieve freshness)
  \end{flushleft}
  Cryptographic Checksum Protects
}

\card{\normalfont
  What are some \textbf{threats} to message security?
}{\normalfont
  \begin{flushleft}
    - Content disclosure \\
    - Traffic flow analysis \\
    - Sender masquerading \\
    - Content modification \\
    - Sequence modification \\
    - Timing modification \\
    - Repudiation of transmission \\
    - Repudiation of receipt
  \end{flushleft}
  Threats to Message Security
}

\card{\normalfont
  What is a \textbf{message digest} function?
}{\normalfont
  Given a message M of arbitrary length, a \textbf{Message Digest} function, H, produces a fixed-size output, h, (called a message digest, checksum, hash value, or fingerprint, of M), i.e. h = H(M). h should be a function of all the bits of M. This is a many-to-one mapping, so collisions are unavoidable, but we should make finding collisions as difficult as we can.
}

\card{\normalfont
  What are the requirements of a \textbf{message digest} function?
}{\normalfont \footnotesize
  \begin{flushleft}
    - \textbf{Compression}: H can be applied to a block of data of any size, but produces a fixed-length output. \\
    - \textbf{One-way property} (preimage resistant): H(x) is easy to compute for any given x. For any given h, it is hard to compute x such that H(x) = h. \\
    - \textbf{Weak collision resistance} (2nd preimage resistant): Given x, it is hard to find y != x such that H(y) = H(x). \\
    - \textbf{Strong collision resistance}(collision resistance): It is hard to find two different messages, x != y such that H(y) = H(x). If H is strong collision resistant, then H is also weak collision resistant.
  \end{flushleft}
  Message Digest Requirements
}

\card{\normalfont
  What are the possible attacks of a \textbf{message digest} function?
}{\normalfont \footnotesize
  \begin{flushleft}
    - Signature forgery if weak collision resistance property is not met: Assuming A has signed a message M; M ll EKRa[H(M)]. \\
      An attacker E intercepts the message and finds another message M' with H(M) = H(M'). E has now A's signature and can use it to send messages pretending to be A \\
    - Repudiation if strong collision resistance property is not met. Assuming that A is to send a signed message M to B. \\
      A chooses two messages M and M’ with H(M)=H(M’); \\
      A signs M by generating signature s=EKRa[H(M)] and sends B M ll s; Later A repudiates this signature, saying it was really a signature on the message M’. \\
      B has no way of confirming that M' != M \\
  \end{flushleft}
  Message Digest Possible Attacks
}

\flashcard{\normalfont
  A \blank{\textbf{Message Authentication Code (MAC)}} has a built in secret key, and is block cipher based. It is a public function with a shared secret key that produces a fixed-length output, i.e. MAC  = fk(M).
}

\card{\normalfont
  What are the properties of using a \textbf{Message Authentication Code (MAC)}?
}{\normalfont \footnotesize
  \begin{flushleft}
    If only A and B know the secret key K, and if MAC = MAC', then the receiver can be assured that: \\
    - The message has not been altered - \textbf{integration protection}; \\
    - The message is from the alleged sender - \textbf{origin authentication}; \\
    - The message is of the proper sequence if the message includes a sequence number; \\
    - The message is \textbf{fresh} (i.e. not a replay, an old message which got sent again): If the message includes a timestamp or a random number contributed (fully or partially) by B (the recipient).
  \end{flushleft}
  MAC Properties
}

\card{\normalfont
  What provides the \textbf{security} of a \textbf{MAC}?
}{\normalfont
  \begin{flushleft}
    - Brute force attacks: Finding collisions, cost 2 (to n/2), where n is the bit-length of the MAC value, the longer the MAC value, the more secure; at least 160-bit MAC. Attack key space or MAC by exploiting MACs with known message-MAC pairs; at least 128-bit MAC. \\
    - Cryptanalysis attacks exploiting weaknesses in algorithms \\
    - Note: A MAC is not a digital signature; it does not provide non-repudiation.
  \end{flushleft}
  MAC Security
}

\flashcard{\normalfont
  A \blank{\textbf{hash function}} doesn't have a built in secret key and is specifically designed.
}

\card{\normalfont
  What is the fundamental \textbf{difference} between a \textbf{MAC} and a \textbf{hash function}?
}{\normalfont
  Fundamental difference between a MAC and a hash function is that a hash function does not have an embedded key. A hash value generated should be protected by a secret (i.e. an asymmetric private key or a symmetric key).
}

\flashcard{\normalfont
  A \blank{\textbf{HMAC}} uses a hash function to construct a MAC function by concatenating a secret to the input of the hash function (Constructs MAC by applying message and key to cryptographic hash function in a nested manner. i.e. HMAC(K, M) = H[(K xor opad) ll H[(K xor ipad) ll M])
}

\card{\normalfont
  \textbf{Authenticated Encryption} achieves both message authentication and confidentiality. What are its possible approaches?
}{\normalfont
  \begin{flushleft}
    - Hash \textit{then} encrypt: E(K, (M ll H(M)); \\
    - MAC \textit{then} encrypt (used in SSl): E(K2, (M ll MAC(K1,M)) or T = MAC(K1, M), E(K2, (M ll Tag)); T here stands for authentication Tag. \\
    - Encrypt \textit{then} MAC (used in IPSec): C = E(K2, M), T - MAC(K1, C); \\
    - Encrypt \textit{and} MAC (used in SSH): C = E(k2, M), Tag = MAC(k1, M). 
  \end{flushleft}
  Authenticated Encryption Approaches
}

\card{\normalfont
  MAC then encrypt, encrypt then MAC, which one is more vulnerable to DoS? 
}{\normalfont
  \begin{flushleft}
    MAC then encrypt is more vulnerable because the receiver has to make a decision whether to receive a message. \\
    The decision is based on the verification of the Tag. \\
    To verify this Tag, one will have to first do a decryption, which for the other one is not necessary. But it can be more secure as it has two keys. \\
  \end{flushleft}
  MAC then Encrypt vs Encrypt then MAC
}

\card{\normalfont
  What are the implications of the performances of the three authentication encryption approaches?
}{\normalfont
  \begin{flushleft}
    For \textit{then} 2 operations done one after the other, while for \textit{and} they can be done at the same time which makes the time a lot shorter than the one for then. \\
    The more overlap the better, which is the essence for authenticated encryption (overlap = pipelining).
  \end{flushleft}
  Differences in Authenticated Encryption Approaches
}


% ================================ Lecture 6 ===================================
\flashcard{\normalfont
  A \blank{\textbf{digital signature}} associates a mark unique to an individual with a body of text (e.g. Only A can sign a message, since only A has access to the private key. Anyone can verify A’s signature, since everyone has access to its public key).
}

\card{\normalfont
  What are the requirements of a \textbf{digital signature}?
}{\normalfont
  \begin{flushleft}
    - \textbf{Message dependent}: Non Reusable and Ensures integrity \\
    - \textbf{Signer dependent}: Unforgeable and Ensures authenticity \\
    - \textbf{Verifiable}: others should be able to verify that the signature is indeed from the originator.
    Both integrity and authenticity are necessary to ensure \textbf{non-repudiation}, i.e. the signer can not falsely deny that they have generated the signature.
  \end{flushleft}
  Digital Signature Requirements
}

\card{\normalfont
  What does a \textbf{digital signature} scheme consist of?
}{\normalfont
  \begin{flushleft}
    - A key generation algorithm \\
    - A signature (generation) algorithm \\
    - A signature verification algorithm
  \end{flushleft}
  Digital Signature Scheme Components
}

\card{\normalfont
  Which are the two well known \textbf{digital signature} schemes?
}{\normalfont
  \begin{flushleft}
    - \textbf{RSA} encryption algorithm can be used in reverse to produce a signature. \\
    - \textbf{DSA} is a signature algorithm based on discrete logarithms. 
  \end{flushleft}
  Digital Signature Schemes
}

\card{\normalfont
  What are the \textbf{differences} between the \textbf{RSA} algorithm and the \textbf{DSA} algorithm?
}{\normalfont \footnotesize
  \begin{flushleft}
    - Security is based on RSA: difficulty of factoring large number and DSA: difficulty of taking discrete logarithms  \\
    - RSA Can encrypt and sign while DSA can only sign messages \\
    - RSA is faster than DSA in signature verification, and about the same in signature generation. In DSA some signature computation can be computed a priori \\
    - RSA can recover the message digest from the signature, while DSA can not. \\
    - DSA: need to choose a unique secret number k for each message
  \end{flushleft}
  RSA vs DSA
}


% ================================ Lecture 7 ===================================
\flashcard{\normalfont
  \blank{\textbf{Public Key Infrastructure (PKI)}} provides functions, technologies policies and services that enable practical deployment and wide-scale application of public-key cryptography (secure public key distribution).
}

\card{\normalfont
  What are the PKI supported \textbf{security services}?
}{\normalfont
  \begin{flushleft}
    - Certificate-based user/entity authentication. \\
    - Digital signing of electronic documents, emails, software for authentication, integrity and nonrepudiation protections. \\
    - Encryption, typically for symmetric key distributions.
  \end{flushleft}
  PKI Supported Security Services
}

\card{\normalfont
  What are some of the common PKI \textbf{applications}?
}{\normalfont
  \begin{flushleft}
    - Web browsers, servers and services, e.g. SSL (secure socket layer). \\
    - Virtual Private Networks (VPNs), e.g. IPSec. \\
    - Secure email services, e.g. S/MIME, PGP (pretty good privacy). \\
    - Secure file storage services, e.g. PGP. \\
    - Secure electronic transactions, e.g. SET. \\
    - Visa Master smartcards. \\
    - Copyright protection (DRM), etc. \\
  \end{flushleft}
  PKI Applications
}

\flashcard{\normalfont
  A \blank{\textbf{digital certificate}} is a statement which certifies that this public key belongs to a this identity, and that the owner with this identity possesses the corresponding private key.
}

\card{\normalfont
  What are the two \textbf{trust models} of PKI?
}{\normalfont
  \begin{flushleft}
    SPKI (Simple PKI): a bottom up approach \\
    - Uses Web-of-trust model. \\
    - Public keys are signed/certified by friends or friends’ friends. \\
    - You are supposed to trust some of the friends. \\
    - Used in the PGP (pretty good privacy) solution. \\
    X509 PKI: a top-down approach \\
    - Public keys are signed/certified by trusted authorities, Certification Authorities (CAs). \\
    - A CA or CA hierarchy digitally sign keys in a top-down manner.
  \end{flushleft}
  PKI Trust Models
}

\card{\normalfont
  Certification is a secure and scalable way of distributing public keys. What does a \textbf{digital certificate} do?
}{\normalfont
  \begin{flushleft}
    - Binds an entity’s public key (+ one/more attributes) to its identity (the entity = person, hardware device, software process). \\
    - Is digitally signed by the CA so you need CA’s public key to verify the certificate. \\
    - Its contents are application dependent, e.g. a certificate for secure email contains the entity’s email address; a certificate for financial purpose may contain credit card number and credit limit, etc.
  \end{flushleft}
  Digital Certificate
}

\flashcard{\normalfont
  \blank{\textbf{Certificate Revocation Lists (CRLs)}} are a  mechanism to let the world know that a certificate is no longer valid. It is a black list of revoked certificates (i.e. prematurely terminated certificates). A CRL is a data structure, digitally signed by the issuing CA, containing: the date and time of the CRL publications; the name of the issuing CA and the serial numbers of all the revoked certificates.
}

\card{\normalfont
  Why isn't using CAs straightforward?
}{\normalfont
  \begin{flushleft}
    - The issuing CA needs to keep the CRL up-to-date. \\
    - A certificate-using application should obtain the most recent CRL and ensure that the certificate serial number is not on the CRL list; in other words, a certificate is said to be valid if and only if the following verifications are positive: it has a valid CA signature; it has not expired; it is not listed in the CA’s most recent CRL. \\
    - There are some scalability issues. That’s why short expiration policies are important.
  \end{flushleft}
  CA not straightforward
}


% ================================ Lecture 8 ===================================
\card{\normalfont
  What is a \textbf{random number}'s definition?
}{\normalfont
  A \textbf{random number}: given an integer, k > 0, and a sequence of numbers, n1, n2, …, an observer can not predict nk even if all of n1, …, nk-1 are known. Physical sources of random numbers are based on nondeterministic physical phenomena, e.g. atmospheric noise; stock market data, etc.
}

\flashcard{\normalfont
  A \blank{\textbf{session key}} is a symmetric (secret) key which is only used for one session.
}

\card{\normalfont
  Why is it desirable to use different session keys in different sessions?
}{\normalfont
  \begin{flushleft}
    - Limit available ciphertexts for cryptanalysis; \\
    - Limit exposure (both in time period and amount of data) in an event of key compromise; \\
    - Avoid long-term storage of a large number of secret keys by only creating them when needed.
  \end{flushleft}
  Reasons for using different session keys for different sessions
}

\card{\normalfont
  What are the two session key establishment solutions?
}{\normalfont \footnotesize
  \begin{flushleft}
    - \textbf{Key agreement (exchange)} protocols: a shared secret is derived by the parties as a function of information contributed by each, such that no party can predetermine the resulting value - Diffie-Hellman (DH) protocol. \\
    - \textbf{Key transportation} protocols: Without any use of a public-key cipher: session keys are generated and distributed with the help of a third party - the Needham-Schroeder protocol. With the use of a public key cipher: One party creates a secret value (session key), and securely transfers it to the other party using the recipient’s public key.
  \end{flushleft}
  Key Establishment Solutions
}

\flashcard{\normalfont
  The \blank{\textbf{Diffie-Hellman}} key exchange (agreement) protocol allows two parties who have never met before to exchange messages in public and collectively generate a key that is private to them, and none of the parties could predetermine the key. Its security is based on the difficulty of calculating discrete logarithms in a finite field.
}

\card{\normalfont
  What kind of attack is the DH protocol vulnerable to, and why?
}{\normalfont
  Neither party knows who it shares the secret with, so it is vulnerable to active, man-in-the-middle attacks.
}

\flashcard{\normalfont
  The \blank{\textbf{Needham-Schroeder}} key distribution (transportation) protocol, without the use of any public-key cipher, session keys are generated and distributed with the help of a third party. The usage of a trusted 3rd party reduces the complexity of the problem from n (to 2) to n, making it more scalable.
}

\card{\normalfont
  What is the distvantage of the Needham-Schroeder protocol?
}{\normalfont
  The distvantage of the Needham-Schroeder protocol is the requirement to trust KDC; KDC has enough information to impersonate anyone, if it is compromised all resources in the system are vulnerable. KDC is a single point of failure and performance bottleneck.
}

\card{\normalfont
  What are the two distribution using PKC solutions and how do they work?
}{\normalfont
  \begin{flushleft}
    1. \textbf{Two passes}: Secret key distribution with mutual authentication using public key cryptosystem + \textbf{timestamps}. \\
    2. \textbf{Three passes}: Symmetric key distribution with mutual authentication using digital signatures + \textbf{nonces} (random numbers).
  \end{flushleft}
  Distribution using PKC solutions
}


% ================================ Lecture 9 ===================================
\flashcard{\normalfont
  \blank{\textbf{Entity authentication}} is the process of verifying a claimed identity. \\
  It provides mutual identification and \textit{authentication}. The user identity is a parameter in access control decisions (\textit{authorisation}) and is recorded when logging security-relevant events in an audit trial (\textit{accounting}). This is the so called \textit{AAA services}.
}

\card{\normalfont
  What are some of the methods used for user identification/ authorisation?
}{\normalfont \small
  \begin{flushleft}
    - Where you are (location authentication, physical location/ specific terminal, e.g. based on IP address). \\
    - Something you know (passwords, PIN). \\
    - Something you have (keys - soft tokens, and hard tokens (smart cards)) - may require special hardware. \\
    - Something you are (biometrics - fingerprint matching, voice recognition, face recognition, iris scanning, etc) require special hardware. \\
    -Combined (or multiple) methods may be used for a higher level of assurance.
  \end{flushleft}
  User identification/ authorisation methods
}

\card{\normalfont
  Which are the prominent schemes for authentication?
}{\normalfont \footnotesize
  \begin{flushleft}
    - Client-server authentication solutions: Password-based authentication or Smart-card-based (token-based) authentication: Symmetric key based or PKI based: Digital signatures and X.509 certificates. \\
    - Enterprise-wide authentication solutions: Kerberos (a password centric solution) and RADIUS (a centralised AAA service). \\
    - Shibboleth (authentication access to multiple enterprises/organisations). \\
    Different authentication schemes = different levels of assurance. There is a trade-off between the level of security vs the complexity vs cost.
  \end{flushleft}
  Authentication Schemes
}

\flashcard{\normalfont
  Unix system chooses not to store plaintext passwords, rather it stores \blank{\textit{encrypted/hashed}} passwords in the password file. Storing passwords for all the system users plainly visible in a password file is vulnerable to theft and accidental disclosure (e.g. due to programming errors). \\
  The \blank{\textit{hashing algorithm}} is a one-way function, called crypt(), that is modified based on the DES algorithm. It uses salt to make the DES-based one-way function different from DES and to make dictionary attacks harder to succeed.
}

\card{\normalfont
  What is the pseudo-code for Unix's \textbf{crypt()} algorithm?
}{\normalfont \footnotesize
  \begin{flushleft}
    - Using DES with first 7 bits of the first 8 characters of passwords as the key. \\
    - Iterated 25 times on constant string 0s; making the process slower. \\
    - Using salt to perturb the DES algorithm, so that: DES chip can not be used to (dictionary) attack the algorithm; and It makes pre-compiled dictionary attacks harder (by a factor of 4,096) \\
    - It prevents an identical password from producing the same encrypted password. \\
    - The final 63 bits are unpacked into a string of 11 printable characters, called the encrypted password.
  \end{flushleft}
  Unix \textit{crypt()} Algorithm
}

\card{\normalfont
  What does the \textit{/bin/passwd} program do when a user creates an account ot changes a password?
}{\normalfont
  \begin{flushleft}
    - Selects a salt based on the time of the day; the DES salt is a 12-bit number, between 0 and 4095, that is converted into a two-character string and is stored in the \textit{/etc/passwd} file along with the encrypted password. \\
    - The password is used as the encryption key to encrypt a block of zero bits using \textit{crypt()} to generate the encrypted password.
  \end{flushleft}
  \textit{/bin/passwd} when creating account or changing password
}

\card{\normalfont
  What happends when a user tries to \textbf{login}?
}{\normalfont
  When a user tries to \textbf{login}, the program \textit{/bin/login} takes the password the user typed, and the salt from the password file, to generate a fresh encrypted password, and compares the newly generated one with the one stored in the \textit{/etc/passwd} file. If the to encrypted results match, the system lets the user in.
}

\card{\normalfont
  The unix password file is \textit{/etc/passwd}. Each entry is for one account and has several fields separated by colons. Which are those?
}{\normalfont \small
  \begin{flushleft}
    - User name: the account name; \\
    - Password: the hashed password preceded by a salt value to be used with the password. Salt make the passwords more difficult to guess and the hashing algorithm slower; \\
    - User ID: a number assigned to this user name for system use in identifying the account; \\
    - Group ID: a number for the user’s group; \\
    - Home Directory; \\
    - Shell: the user’s default shell program.
  \end{flushleft}
  \textit{/etc/passwd} fields
}

\flashcard{\normalfont
  The attack where an attacker can eavesdrop on a network to get our login ID and encrypted password and later replays (re-sends) it to gain access to the network is called a \blank{\textbf{replay attack}}.
}

\card{\normalfont
  How does the \textbf{replay attack} work?
}{\normalfont \small
  \begin{flushleft}
    In order to perform this attack, the attacker needs to: \\
    - Modify the client/logon software so that it does not encrypt the encrypted password, but rather replay it directly; \\
    - Eavesdrop on the network (or access to the password file) \\
    Usually we assume that: \\
    - The LAN is secure, i.e. eavesdropping can be noticed \\
    - You do not bring your own client software in \\
    So we tend to overlook this problem in LAN environment.
  \end{flushleft}
  The Replay Attack
}

\flashcard{\normalfont
  A \blank{\textbf{one-time password}} is a password that can only be used once, and that thwarts sniffing and replay attacks.
}

\card{\normalfont
  What are the approaches of the \textit{one time password}?
}{\normalfont
  \begin{flushleft}
    Challenge response \\
    - Random number based OTP \\
    - Clock based OTP (need token) but the clock has to be reliable, and secure; and the clocks between the entities must be synchronised. \\
    - Counter-based OTP (need token) \\
    - If a hard token is used, then it should be locked with a PIN or password. \\
    S/Key
  \end{flushleft}
  One-time Password Approaches
}

\flashcard{\normalfont
  A \blank{\textbf{smart card}} is an authentication token that a person carries around and uses in authenticating.
}

\card{\normalfont
  What are the advantages and disatvantages of using a \textbf{smart card}?
}{\normalfont \footnotesize
  \begin{flushleft}
    Advantages: \\
    - Unlike memory cards, they can do more than just containing some secret information; they can perform simple crypto operations. \\
    - Support mobility, can ‘memorise’ your secret, and can provide two factor authentication. \\
    Disadvantages: \\
    - Smart-cards require special hardware reader on every access device, which may be expensive and requires standardisation. \\
    - They are subject to theft, so used in conjunction with some other authentication mechanisms such as PIN/password.
  \end{flushleft}
  Pro and Con for using a Smart Card
}

\flashcard{\normalfont
  The \blank{\textbf{man-in-the-middle attack}} consists of a third person posing as A to b and as B to A.
}

\card{\normalfont
  What is the \textbf{X.509 Certificate Based Authentication Service}, and what does it do?
}{\normalfont \small
  \begin{flushleft}
    - It defines a framework - a system to enable the validation of, and to give legal meaning to, digital signatures (which require the use of hash functions). \\
    - It allows mutual authentication using public key technology - digital signatures and digital certificates. \\
    - It does not dictate the use of a specific public-key cryptographic algorithm but recommends RSA, nor does it define a specific hash algorithm. \\
    - It is used in S/MIME, IP Security, SSL/TLS and SET.
  \end{flushleft}
  X.509 Certificate Based Authentication Service
}

\card{\normalfont
  How does the \textbf{challenge-response authentication method} work using \textbf{public keys}?
}{\normalfont
  \begin{flushleft}
    - As only B can decrypt the random number (nonce), r1, correctly, the message (2) authenticates B to A. \\
    - Message (3) authenticates A to B. \\
  \end{flushleft}
  Challenge-response Authentication method with Public Keys
}

\card{\normalfont
  How does \textbf{challenge-response authentication method} work using \textbf{digital signatures}?
}{\normalfont
  \begin{flushleft}
    - As only B can generate the rightful signature, message (2) authenticates B to A. \\
    - Message (3) authenticates A to B.
  \end{flushleft}
  Challenge-response Authentication method with Digital Signatures
}

\flashcard{\normalfont
  \blank{\textbf{Enterprise Authentication}} is a central authentication for a number of systems in an organisation. It has one central authority (security server) at a site to manage all the passwords instead of each computer having its own. By this, we can enforce organisation wide security policies, including authentication, authorisation and accounting (i.e. the AAA services). The security server is responsible for providing AAA services to edge devices, e.g. VPN servers and wireless access points.
}

\card{\normalfont
  What are some examples of \textbf{systems} for \textbf{enterprise authentication}?
}{\normalfont
  \begin{flushleft}
    - Radius: remote authentication for dial-in user services. Initially used for providing authentication services for one or more access servers. Later extended to handle enterprise AAA services.\\
    - Kerberos
  \end{flushleft}
  Enterprise Authentication Systems
}

\card{\normalfont
  What is the \textbf{RADIUS} protocol?
}{\normalfont \footnotesize
  \begin{flushleft}
    Client forwards the user access request to a RADIUS server \\
    The Server: \\
    - Replies with reject access or allow access based upon a user supplied password/credential. \\
    - Challenge (when challenge-response protocol is used, e.g. CHAP). \\
    - If challenge-response is used, client forwards Challenge to the user, and the user sends their response to the client that then forwards it to the server. \\
    - One RADIUS server may act as a client to another RADIUS server for consultation, etc.
  \end{flushleft}
  RADIUS Protocol
}


% =============================== Lecture 10 ===================================
\flashcard{\normalfont
  A \blank{\textbf{Virtual Private Network (VPN)}} is a security solution, making use of tunneling, encryption, authentication, and access control technologies to allow you to achieve private communication over public networks such as the Internet.
}

\flashcard{\normalfont
  \blank{\textbf{Tunneling}} includes encapsulation, transmission and decapsulation; \textbf{encapsulation} is to wrap data with a header that provides routing information allowing it to transmit across the Internet to reach its destination so as to emulate a dedicated point-to-point link.
}

\flashcard{\normalfont
  \blank{\textit{VPN Routers/ Gateways}} are located at the corporate network perimeter; they perform tunneling, authentication, and data encryption/ decryption.
}

\card{\normalfont
  What are the two types of \textbf{VPN Router/ Gateways}?
}{\normalfont
  \begin{flushleft}
    - \textbf{Standalone VPNs} incorporate purpose-built devices. \\
    - \textbf{Integrated} implementations add VPN functionality to existing devices such as routers and firewalls. \\
    --- \textit{Router based VPNs} add encryption support to existing routers and can keep the upgrade costs of VPN low. \\
    --- \textit{Firewall based VPNs} are workable solutions for small networks with low traffic volume.
  \end{flushleft}
  Types of VPN Routers/ Gateways
}

\flashcard{\normalfont
  A \blank{\textbf{VPN Client}} is software used for remote VPN access. It creates a secure path from the remote client computer to a VPN gateway. It can be loaded onto an individual computer requesting remote access \textbf{or} a router that establishes a peer-to-peer (router-to-router) VPN connection.
}

\card{\normalfont
  During tunnel setup, the devices on each side of the tunnel agree on the details of \textbf{authentication} and  \textbf{encryption?}. What do these do?
}{\normalfont
  \begin{flushleft}
    - \textbf{Authentication} is for identifying VPN users and devices and for ensuring the authenticity of data; \\
    - \textbf{Encryption} is for protecting the confidentiality of data while transit across the Internet.
  \end{flushleft}
  VPN Authentication and Encryption
}

\card{\normalfont
  What are some of the \textbf{security risks} on the \textbf{internet}?
}{\normalfont
  \begin{flushleft}
    - Loss of privacy (packet sniffing): a perpetrator may observe confidential data as it traverses the Internet. (Confidentiality - Encryption) \\
    - Loss of data integrity: data may be modified maliciously or accidentally. (Integrity - HMAC) \\
    - Identity spoofing: impersonation. (Entity Authentication - Keyed hash token) \\
    - Denial of Service: attacks to cause computer systems to crash.
  \end{flushleft}
  Security Risks on the Internet
}

\card{\normalfont
  What are the multiple ways of implementing a VPN?
}{\normalfont
  \begin{flushleft}
    - PPTP (point-to-point tunneling protocol) is based upon PPP (point-to-point protocol). \\
    - L2TP (Layer 2 tunneling protocol) is an extension or enhanced version of PPTP; often used together with IPSec. \\
    - IPSec \\
    Although IPSec has become the facto standard for LAN-WAN-LAN VPNs, PPTP and L2TP are heavily used for single client LAN connections. Therefore, many VPN products support IPSec, PPTP and L2TP.
  \end{flushleft}
  Ways to Implement a VPN
}

\card{\normalfont
  What are the properties of \textbf{IPSec}?
}{\normalfont \small
  \begin{flushleft}
    It operates at the IP (network) layer. \\
    It provides security protection
    - For the transport layer, including TCP and UDP, traffic; \\
    - For all other traffic carries in the data files of the IP packet, e.g. ICMP messages; \\
    - Also for IP packets (IPv4 and IPv6) when using tunnel mode. \\
    The protection is transparent, i.e. there is on need to modify applications or transport-layer protocols to work with IPSec, and can be applied to all the application level programs.
  \end{flushleft}
  IPSec Properties
}

\flashcard{\normalfont
  \blank{\textbf{Security Association (SA)}} refers to a set of attributes negotiated between two end-points for the protection of IP traffic for it:   Authentication mechanism (Default HMAC), Encryption algorithm and Algorithm mode (default DES-CBC), A shared session key, Initialisation Vector (IV), etc. \\
  It is \textit{unidirectional}, so for two-way secure exchange two \blank{SAs} are needed. \\
  Is uniquely identified by:\\
  - A random 32-bit value SPI (secure parameter index);\\
  - Destination (tunnel ending point) IP address; \\
  - An identifier of the security protocol (AH or ESP).
}

\card{\normalfont
  What are the to types of \textbf{key management}?
}{\normalfont \footnotesize
  \begin{flushleft}
    1. Manual management: \\
    - Manually configure keying material and SA data for each system; \\
    - Practical in small, static environments; does not scale well. \\
    2. Automated key management \\
    a. ISAKMP (Internet SA key Management Protocol): Defines procedures and packet formats to establish, negotiate, modify and delete SA. \\
    b. IKE (Internet Key Exchange): Provides facilities to negotiate and derive keying material for establishing a session key
    - DH-DSA: using Diffie-Hellman (DH) key agreement for deriving key material between peers on a public network, and DSA to sign the DH exchanges to counter the man-in-the-middle attack.
    - Public key cryptography: using recipient’s public key for secure session key transportation.
  \end{flushleft}
  Key Management Types
}

\card{\normalfont
  What are the three different types of authentication methods that the ISAKMP/IKE supports?
}{\normalfont
  \begin{flushleft}
    1. Symmetric key cryptography: The same key is pre-installed on each host. The peers authenticate each other by computing and sending a keyed hash of data that includes the pre-shared keys.\\
    2. Public key cryptography\\
    3. Digital Signature: Each device signs some data contributed by the other entity; This method is similar to scheme teo, except that it does provide non-repudiation; Both RSA and DSS are supported.
  \end{flushleft}
  ISAKMP/IKE Authentication Methods
}

\card{\normalfont
  What are the properties of the ISAKMP/IKE public key cryptography authentication method?
}{\normalfont \footnotesize
  \begin{flushleft}
    - Each party generates a pseudo-random number (nonce) and encrypts it and its ID using the other party’s public key;\\
    - The ability to decrypt the data with the local private key authenticates the parties to each other. \\
    - The method requires the ability to generate random numbers, and perform public-key encryption/decryption; \\
    - It does not provide non-repudiation (as in scheme one). \\
    - Currently, only RSA algorithm is supported.
  \end{flushleft}
  SAKMP/IKE Public Key Cryptography Authentication Method
}

\flashcard{\normalfont
  Once SA(s) is negotiated and session key established, packets are forwarded using \blank{\textbf{traffic protocols}}, \blank{\textbf{AH}} and/or \blank{\textbf{ESP}}.
}

\flashcard{\normalfont
  IPSec (AH and ESP) may be employed in one of the two ways: \blank{\textbf{transport}} and \blank{\textbf{tunnel}} modes (or a combination of them).
}

\card{\normalfont
  Multiple SAs may be combines into an SA bundle. An SA can only implement either AH or ESP. In what acses would one want to combine more SAs into a bundle?
}{\normalfont
  \begin{flushleft}
    - To have both services; and/or \\
    - Different flows in one communication path requires different services.
  \end{flushleft}
  Reasons for Combining Multiple SAs into a Bundle
}

\card{\normalfont
  In what ways can SAs be combined into a bundle?
}{\normalfont
  \begin{flushleft}
    1. Transport Adjacency: \\
    - Apply ESP in transport mode without authentication; \\
    - Apply AH in transport mode. \\
    2. Iterated Tunneling (multiple nested tunnels): \\
    - Use multiple IPSec services through IP tunneling; multiple SAs in one bundle mau terminate at different or same endpoint.
  \end{flushleft}
  Ways of Combining SAs into a Bundle
}

\card{\normalfont
  Each of the IPSec traffic protocols defines a new set of headers to be added to IP datagrams. Which are those?
}{\normalfont \footnotesize
  \begin{flushleft}
    - Authentication Header (AH) provides: Data origin authentication, Data integrity, Anti-replay, Does not provide confidentiality protection. \\
    - Encapsulating security payload (ESP) provides: Confidentiality (encryption) protection, Partial traffic flow confidentiality (Optional service: Data origin authentication, Data integrity, Anti-replay). \\
    - Uses keyed-hash function, HMAC, for data integrity and authentication protection (no non-repudiation protection): \\
    - Uses bulk encryption algorithms, 3-key triple DES, AES, IDEA, CAST, Blowfish and RC5, for confidentiality protection.
  \end{flushleft}
  IPSec Traffic Protocols
}

\card{\normalfont
  What is the format of the \textbf{Authentication Header (AH)} of \textbf{IPSec}?
}{\normalfont \small
  \begin{flushleft}
    - NextHeader: specifies the type of header immediately following the Authentication Header. \\
    - PayloadLength: the length of AH in 4-byte unit, minus ‘2’. \\
    - Reserved: not used for now, (set to 0). \\
    - SPI (security Parameter Index): identifies a SA. \\
    - SequenceNumber: contains a monotonically increasing counter to protect against replay. \\
    - AuthenticationData: contains the message authentication code (MAC) for this packet (typically 96 bits long).
  \end{flushleft}
  IPSec's AH Format
}

\card{\normalfont
  What is the MAC computation?
}{\normalfont \footnotesize
  \begin{flushleft}
    The default MAC algorithm is HMAC built on keyed one-way hash function (MD5 or SHA-256 - which is detailed in the SA). It is truncated to the first 96 bits. It is stored in the AH AuthenticationData field. \\
    The following rules are applied to IP Headers (transport mode) and New IP Headers (tunnel mode) when computing the MAC:\\
    - Mutable IP header fields are zeroed prior to MAC calculation. All other (immutable) fields are included. \\
    - The AH AuthenticationData field is zeroed. All other AH header fields are included. \\
    - The entire upper-level protocol data are included.
  \end{flushleft}
  MAC Computation
}

\card{\normalfont
  What are the \textbf{Integriy and Authentication Services}?
}{\normalfont \footnotesize
  \begin{flushleft}
    Outbound packet processing (by sender): \\
    - SA lookup \\
    - Sequence number generation - must not cycle for anti-replay \\
    - MAC calculation \\
    Inbound packet processing (by receiver): \\
    - Re-assembly (if IP packet has been fragmented) \\
    - SA lookup \\
    - Sequence number verification \\
    - MAC verification: Computes MAC and verifies that it is the same as the MAC included in AuthenticationData field.
  \end{flushleft}
  Integrity and Authentication Services
}

\flashcard{\normalfont
  \blank{\textbf{Replay}} retransmits a packet to the intended destination.
}

\card{\normalfont
  What does \textbf{anti-replay} do?
}{\normalfont \footnotesize
  \begin{flushleft}
    - The SequenceNumber field of an AH is used to thwart replay attacks. \\
    - For a new SA, sequence number is initialised as 1 for the 1st packet, and increate it by 1 for each outgoing packet ( up to 232 - 1). If this limit is reached, the a new SA with a new key should be negotiated. \\
    - IP service is connectionless and unreliable, but IPSec requires the receiver implement a (default) window of size W = 64 to track the out-of-order packets received, and to ensure that old or duplicated/replayed packets are discarded.
  \end{flushleft}
  Anti-replay
}

\card{\normalfont
  How does \textbf{anti-replay} work?
}{\normalfont \small
  \begin{flushleft}
    - A window size, W, specifies number of out-of-order packets that are tracked. The right edge of the window shows the highest sequence number, N, of the packet received so far. \\
    - For packet with sequence numbers in the range from N - W + 1 to N: if MAC is correct, then mark it; otherwise, drop. \\
    - If a received packet is to the right of the window and is correctly authenticated, mark the packet and advance the window. If a received packet is to the left window, drop the packet.
  \end{flushleft}
  Anti-replay and how it works
}

\card{\normalfont
  What is the format of the \textbf{Encapsulating Security Payload (ESP)} of \textbf{IPSec}?
}{\normalfont \footnotesize
  \begin{flushleft}
    - PayloadData: is a transport level segment, e.g. TCP segment, (transport mode), or IP packet (tunnel mode) that is protected by encryption. \\
    - Padding: to expand the plaintext (consisted of PayloadData, Padding, PadLth, NextHdr) to the required length and to provide partial traffic flow confidentiality. \\
    - PadLth: indicates the number of pad bytes immediately preceding it. \\
    - NextHdr: identifies the type of data contained in the PayloadData field by identifying the first header in that payload. \\
    - AuthenticationData: contains MAC computed over the ESP packet minus it.
    Other headers are the same as in AH.
  \end{flushleft}
  IPSec's Encapsulating Security Payload (ESP) Format
}

\card{\normalfont
  How does IPSec's ESP outbound packet processing look like?
}{\normalfont
  \begin{flushleft}
    - SA lookup \\
    - Packet encryption \\
    --- Encapsulate relevant data into the ESP payload field. \\
    --- Add any necessary padding. \\
    --- Encrypts the result (PayloadData, Padding, PadLength, and NextHeader) using the key, encryption algorithm indicated by the SA. \\
    - Sequence number generation. \\
    - MAC calculation (if authentication is selected by the SA).
  \end{flushleft}
  IPSec's ESP Outbound Packet Processing
}

\card{\normalfont
  How does IPSec's ESP inbound packet processing look like?
}{\normalfont
  \begin{flushleft}
    - Re-assembly (if IP packet has been fragmented by the routers en route) \\
    - SA lookup \\
    - Sequence number verification \\
    - MAC verification \\
    - Packet decryption: \\
    --- Decrypt the relevant data. \\
    --- Process any padding as specified in the encryption algorithm specification. \\
    --- Reconstructs the original IP datagram.
  \end{flushleft}
  IPSec'sESP Inbound Packet Processing
}


% =============================== Lecture 11 ===================================
\flashcard{\normalfont
  \blank{\textbf{Hardware Security Modules (HSMs)}} are more difficult to tamper with so can increase the overall system security level; it can also be designed to accelerate cryptographic functions (asymmetric and symmetric cryptographic operations, key generation, etc.).
}

\card{\normalfont
  What are some drawbacks of \textbf{Software-Only (SW)} solutions?
}{\normalfont
  \begin{flushleft}
    - Certificate and private key are stores in conventional media: not secure. \\
    - Consumers are tied to their PCs: not mobile. \\
    - Consumers need to manage certificates: not simple.
  \end{flushleft}
  Drawbacks of Software-only Solutions
}

\card{\normalfont
  \textbf{Smart cards}, a category of HSMs, support mobility, and are therefore secure portable devices. However, they are limired in capacity so the best approach is to combine them with software in order to get the best of both. How is this combination achieved?
}{\normalfont
  \begin{flushleft}
    - Use SW for bulk symmetric data encryption/decryption \\
    - Use smart card for: key generation/storage, digital envelope retrieval and signature generation.
  \end{flushleft}
  Combination of Smart Cards and Software-Only Solutions
}

\card{\normalfont
  What are the types of \textbf{smart cards}?
}{\normalfont \footnotesize
  \begin{flushleft}
    1. \textbf{Memory cards}: Contain EEPROM (holds data that changes with time, e.g. in prepaid phone cards, it holds talk time left) and ROM (holds card number, card holder name). \\
    2. \textbf{Chip and PIN cards}: On-board memory (RAM, ROM, and EEPROM). On-board Crypto coprocessor for performing crypto operations, random number generator for key generations, and intelligence for making decisions. Provides robust security so difficult to tamper with and uneconomical to counterfeit. Supports multiple applications (e.g. ePayment, ePassport, eIDs, Health, Transport, etc.) \\
    3. \textbf{Interface}: Contact and Contactless (using RFID; commonly seen in mobile payment solutions and ePassport, etc.) \\
    4. \textbf{Hybrid}: Operating System (OS), Java Cards, Multos
  \end{flushleft}
  Types of Smart Cards
}

\flashcard{\normalfont
  \blank{\textbf{EuroPay, MasterCard and Visa (EMV)}} is a standard for smart card based payments (Chip and PIN technology) to replace mag-stripe cards. \\
  It was jointly developed by Europay, MasterCard and Visa for both contact and contactless cards (Using RFID). \\
  It is a self-contained standard, but the physical and electrical aspects are based on ISO/IEC 7816. \\
  It uses electronic authentication to replace hand signatures.
}

\card{\normalfont
  What are th EMV \textbf{security techniques}?
}{\normalfont \footnotesize
  \begin{flushleft}
    1. Card-to-terminal authentication \\
    a. Static Data Authentication (SDA): static authentication data on card is signed with issuer’s private key. \\
    b. Dynamic Data Authentication (DDA): use a terminal generated nonce. \\
    c. RSA digital signatures and digital certificates. \\
    2. Transaction confidentiality/integrity protections: used between the Issuer’s host system and the smart card\\
    - Encryption using 3DES-CBC (for confidentiality) and MAC (SHA-1) for integrity and authenticity. \\
    3. PIN encryption at point of entry (optional service): PIN encrypted using Card’s public key, or Card’s PIN encryption public key
  \end{flushleft}
  EMV Security Techniques
}

\card{\normalfont
  Why is the \textbf{MasterCard SecureCode Solution} needed?
}{\normalfont
  \begin{flushleft}
    Need for a solution to prove that the cardholder (CH) has conducted and authorised the transaction in a virtual, non-face-to-face environment thereby reducing chargebacks and expenses associated with disputed transactions. \\
    SecureCode is such a secure payment solution providing this proof; it is based on the “3-Domain Secure” model.
  \end{flushleft}
  Need for MasterCard SecureCode Solution
}

\card{\normalfont
  What are the main features of the \textbf{3-D Secure Model}?
}{\normalfont \small
  \begin{flushleft}
    - It uses SSL technology to protect transaction confidentiality, and to authenticate major parties involved in an online transaction thus supporting secure transactions over the Internet; \\
    - It authenticates CHs in real-time and without using digital certificates: Requires the Ch to answer a challenge in real-time (challenge is from the issuing bank, not the merchant). Issuing bank then confirms the CH’s identity to merchant using a signed token. \\
    - The signed token is the evidence of the cardholder’s authorisation of a payment transaction.
  \end{flushleft}
  3-D Secure Model Features
}

\card{\normalfont
  What are the domains of the 3-D Secure Mode?
}{\normalfont \small
  \begin{flushleft}
    - \textbf{Issuer Domain}: responsible for enrolment of the issuer’s cardholders in the service, and authentication of the cardholders in real-time during online purchase. \\
    - \textbf{Acquire Domain}: ensures that the participating merchant operates under a merchant agreement, and validates the digital signature on purchase requests that have been successfully authenticated by the issuer. \\
    - \textbf{Interoperability Domain}: facilitates the transaction exchange between the other two domains with a common protocol and shared services.
  \end{flushleft}
  3-D Secure Mode Domains
}

\flashcard{\normalfont
  \blank{\textbf{Enrolment}} is a process for collecting a cardholder’s (CH’s) relevant identification and personal information such as a password and a Personal Assurance Message. Once the data is collected and verified (i.e. the CH is enrolled), the data is passed to the Issuer’s Access Control Server (ACS). Each time the CH conducts a transaction; this ACS is queried.
}

\card{\normalfont
  What does the \textbf{Access Control Server (ASC)} do?
}{\normalfont
  \begin{flushleft}
    - Verifies whether a given account number is encrolled. \\
    - Performs the actual CH authentication process during purchase. \\
    - Signs and returns the authN outcome to merchant.
  \end{flushleft}
  Access Control Server
}

\flashcard{\normalfont
  \blank{\textbf{Sirectory Server}} provides centralised decision-making capabilities for merchants, e.g. to help merchants identify and query the issuer about its 3-D Secure capability. \\
  \blank{\textbf{Transaction History Server}} is for logging transaction records, e.g. Payer Authentication Responses; currently it is not implemented by the MasterCard SecureCode infrastructure.
}

\card{\normalfont
  What does the \textbf{directory server} do?
}{\normalfont \small
  \begin{flushleft}
    - Upon CH purchase request, the merchant sends an Enrolment Verification Request message containing CH’s personal account number (PAN) to the Directory Server (DS). \\
    - DS will first determine whether the issuer is 3-D enabled, and if yes, query the issuer if authentication is available for PAN. \\
    - DS forwards the ACS’ response (containing ACS web address), or its own response (if no appropriate ACS is available), to MPI.
  \end{flushleft}
  Directory Server
}

\flashcard{\normalfont
  \blank{\textbf{Merchant Plug-In (MPI)}} is an application software capable of processing 3-D Secure messages and interoperable with the MasterCard SecureCode infrastructure; it creates and processes payer authentication messages.
}

\card{\normalfont
  What are the usual tasks that the Merchant Plug-In (MPI) performs?
}{\normalfont \small
  \begin{flushleft}
    - Identifies the account number, and queries DS to determine if (1) card issuer has participated 3-D Secure and (2) the card is enrolled to the 3-D Secure service; \\
    - If yes, it creates a Payer Authentication Request and sends it to the ACS via CH’s browser to request ACS-CH authentication. \\
    - Verifies the signed Payer Authentication Response returned by ACS containing the authentication outcome and a SecureCode specific token, or DS’ response (if the account number is not 3-D Secure enabled). \\
    - Returns control to the merchant software for further authorisation processing.
  \end{flushleft}
  Merchant Plug-In (MPI) Tasks
}

\flashcard{\normalfont
  \blank{\textbf{Accountholder Authentication Value (AAV)}} is a MasterCard SecureCode specific token. It is generated by issuer and passed to merchant. If CH authentication is successful, the merchant will place the token in its authorisation request sent to the Acquirer. \\
  In the event when there is a chargeback or other potential dispute, the \blank{AAV} will be used as the evidence to identify the processing parameter associated with the transaction.
}

\card{\normalfont
  What are some of the informations that the \textbf{Accountholder Authentication Value (AAV)} includes?
}{\normalfont
  \begin{flushleft}
    - The issuer ACS that created the AAV.\\
    - The sequence number that can be used to positively identify the transaction within the universe of transactions for that location. \\
    - A Message Authentication Code (MAC) generated using a secret key, which will not only ensure AAV data integrity but also bind the entire AAV structure to a specific PAN.
  \end{flushleft}
  Accountholder Authentication Value (AAV) Information
}

\card{\normalfont
  What are the problems of \textbf{email security}?
}{\normalfont
  \begin{flushleft}
    - Lack of confidentiality:
    --- Sent in cleartext over open networks. \\
    --- Stored in cleartext on client machines and servers. \\
    - Lack of integrity: Both the header and content can be modified during transit or while in storage. \\
    - Lack of authenticity (origin authentication and integrity): The sender of an email can be forged. \\
    - Lack of non-repudiation:
    --- The sender can later deny having sent an email. \\
    --- The recipient can later deny having received the email.
  \end{flushleft}
  Email Security Problems
}

\card{\normalfont
  What are \textbf{segmentation} \textbf{reassembly} in terms of \textbf{email security}?
}{\normalfont
  \begin{flushleft}
    Email systems often limit the size of a message up to 50,000 octets. So, a longer message must be broken up into segments. After all other operations, PGP automatically subdivides a long message into small segments. \\
    Once getting those emails, the receiver first strips of all email headers and reassemble the block, and then perform other processing.
  \end{flushleft}
  Email Security Segmentation and Reassembly
}

\card{\normalfont
  What are \textbf{Key Identifiers (Key IDs)} used for?
}{\normalfont
  \begin{flushleft}
    - One user usually uses, or has access to, more than one public/private key pairs. \\
    - A recipient can identify which public key should be used for an incoming message by: \\
    --- Sending the public key with the message, or \\
    --- Use a key identifier to identify a particular key. \\
    - PGP uses the latter approach, i.e. use a user ID plus a key ID to identify a public key. \\
    Key ID = (KUa mod 2 (to 64), i.e. the least significant 64 bits of the public key.
  \end{flushleft}
  Key Identifiers Usage
}

\card{\normalfont
  Each user maintains a pair of data structures (i.e. a pair of key rings) in their system. Which are these?
}{\normalfont
  \begin{flushleft}
    - A \textbf{private-key ring} to store the private/public key pairs owned by the user. \\
    - A \textbf{public-key ring} to store the public keys of others users known to this user. \\
    Both key rings can be indexed by either User ID or Key ID.\\
    The user’s private key is encrypted using the symmetric algorithms, CAST-128 (128-bit key), and the key-encryption key is the first 128 bits of the hash code of a passphrase, Pi, chosen by the user.
  \end{flushleft}
  User System Data structure Pair
}