% ====== Web Frameworks/ MVC Architectural Design Pattern ======

\flashcard{
  \blank{MVC architecture} is a basic pattern where you separate the model (data), view (display), and controller (logic) into different files and directories.
}

\flashcard{
  \blank{Models} represent knowledge. Could be a single object or a structure of objects.
}

\flashcard{
  A \blank{view} is a (visual) representation of its model
}

\flashcard{
  The \blank{controller} is the link between the user and the system.
}

\flashcard{
  With the MVC Design Pattern, \blank{Model} objects encapsulate the data, doesn't communicate directly with View \& defines the logic, manipulation and processing of the data.
}

\flashcard{
  With the MVC Design Pattern, \blank{View} objects present the data and enables user interaction with it. It communicates with controller, notified about changes in data \& controller notifies of any user-made changes.
}

\card{
  What are the benefits of the MVC architecture?
}{
  \begin{flushleft}
    - More reusable: use the same View for multiple application \\ 
    - Easily adaptable: Each object has a clearly defined role. Good design principle
  \end{flushleft}
  Benefits of the MVC architecture
}

% ====== User Interface Design ======

\card{
  What are the stages of UX design?
}{
  $Sketches \longrightarrow Wireframe \longrightarrow Mockups \longrightarrow Prototypes$
}

\card{
  Why would you produce Mock-ups in the first place?
}{
  \begin{flushleft}
    - Dialogue with customers; can be used to confirm requirements, show different choices \& exchange ideas. \\ 
    - Acts as a form of testing, by preventing misunderstanding and removing bugs early.
  \end{flushleft}
  Reasons for Mockups
}

\card{
  What are the 8 golden rules of user interface design?
}{
  \begin{flushleft}
    Strive for consistency \\ 
    Seek universal usability \\
    Offer informative feedback \\
    Design dialogues that bring closure \\
    Prevent errors \\
    Permit easy reversal \\ 
    Keep Users in control \\
    Reduce short term memory load
  \end{flushleft}
  8 golden rules
}

% ====== Modelling Data ======

\flashcard{
  In Spring “model” and “\blank{entity}” used interchangeably.
}

\card{
  In the context of Spring, what is a \textbf{Repository}?
}{
  Data lives in a repository. Repositories are the Spring Mechanism for querying the underlying DB. We used CRUD (Create, Read, Update, Delete) repository.
}

% ====== Security ======
\card{
  What is web app security mainly protecting?
}{
  Assets, which can either be tangible items such as a web page or a customer database, or intangible such as a company's reputation.
}

\card{
  In the context of web app, what does security mainly rely on?
}{
  Authentication and authorization. It also relies on auditing, confidentiality, integrity and availability.
}

\flashcard{
  A \blank{threat} is any potential occurrence, malicious or otherwise, that could harm an asset.
}

\flashcard{
  A \blank{vulnerability} is a weakness that makes a threat possible.
}

\flashcard{
  An \blank{attack} is an action that exploits a vulnerability or enacts a threat.
}

\card{
  Give examples of web app vulnerabilities.
}{
  Code injection: malicious executable code inserted into legitimate traffic sent to an endpoint. \\
  Broken authentication and session management: compromising user identities in a variety of ways. \\
  Cross-site scripting: similar to code injection, but involving scripts instead, drawn from inappropriate sources. 
}

\card{
  What are the main causes of vulnerabilities?
}{
  Poor programming in which exceptions, boundaries, credentials, etc., weren’t considered adequately.
}

\card{
  What are the goals of Computer/network security hinges?
}{
  Keeping unauthorized persons from gaining access to resources. \\
  Ensuring that authorized persons \textit{can} access the resources they need.
}

\card{
  What is authentication?
}{
  The process of recognizing a user's identity. It is the mechanism of associating an incoming request with a set of identifying credentials.
}

\card{
  Examples of authentication methods are?
}{
  \begin{flushleft}
  An ID / password \\
  A PIN (Personal Identification Number) code \\
  An RFID card \\
  Biometrics (usually considered the safest) \\
    – Fingerprints \\
    – Face Recognition \\
  A USB token \\
  A one-time password token\\
  \end{flushleft}
  A lot of sites now use two-factor authentication
}

\card{
  What is authorization?
}{
  Authorization is a security mechanism to determine access levels or user/client privileges related to system resources including files, services, computer programs, data and application features. 
}

\flashcard{
  \begin{flushleft}
    - \blank{Admin}: can access everything. \\ 
    - \blank{HR staff}: can access employee records and other relevant documents. \\
    - \blank{Guest}: very limited access, usually don't need authentication. \\
  \end{flushleft}
  The User Roles
}

% ====== Testing Functionality in Isolation ======

\card{
  What are some important features of unit testing?
}{
  Test’s don’t build on other tests. They test one thing. Stay within class/process/network boundaries - don’t test database as a side effect.
}

\card{
  Integration Testing: Testing the system from end to end. What are the steps?
}{
  Client submits a request to the web server. Web server maps request to a controller. Controller gets data via the DAO layer which gets data from DB. Controller passes data to view. View is processed. Web server sends view to client.
}

\flashcard{
  \blank{Dummy} objects are passed around but never actually used. Usually they are just used to fill parameter lists.
}

\flashcard{
  \blank{Fake} objects actually have working implementations, but usually take some shortcut which makes them not suitable for production.
}

\flashcard{
  \blank{Stubs} provide canned answers to calls made during the test, usually not responding at all to anything outside what's programmed in for the test.
}

\flashcard{
  \blank{Mocks} are pre-programmed with expectations which form a specification of the calls they are expected to receive. They can throw an exception if they receive a call they don't expect and are checked during verification to ensure they got all the calls they were expecting.
}

% ====== Integrating external Services ======

\card{
  What is Spring Social?
}{
  Framework of Spring Boot; establishes connections between Spring boot apps and SaaS(Software as a service) providers e.g. Twitter, Facebook. \\
  $SaaS = API + resources + Interface$
}

% ====== Meeting Customer Requirements ======

\flashcard{
  An \blank{acceptance test} is ablsnk formal description of the behavior of a software product, expressed as a example or a usage scenario.
}

\card{
  What are the benefits of \textbf{Acceptance Tests}?
}{
  \begin{flushleft}
    Closer collaboration between developers and user/customer \\
    Providing clear and unambiguous “contract” \\
    Decrease chance and severity of defects 
  \end{flushleft}
  Acceptance tests benefits
}

\flashcard{
  Authentication = \blank{connection} + \blank{sign-in}.
}

% ====== RESTful WebServices and Test Driven ======

\flashcard{
  \blank{Representational State Transfer (REST)} is an architectural style that is the underlying architectural principal of the WWW. Clients can operate without knowing anything about \blank{the server} \& \blank{the server's resources}. Client and server must agree on the \blank{media type} used.
}

\card{
  What are the two fundamental rules of TDD?
}{
  Write new code only if a test has failed \\
  Eliminate Duplication
}

\card{
  What are the mplications of TDD?
}{
  Developers must write the unit tests \\
  Development environment must provide quick feedback \\
  System must consist of many loosely coupled components: Makes testing easy \\
  Design must be “organic”: Running code provides feedback between decisions
}

\card{
  What does \textbf{RED}, \textbf{GREEN} \& \textbf{REFACTOR} mean in the context of \textbf{Test Driven Development (TDD)}? 
}{
  \begin{flushleft}
    - Write a test that does not work (RED) \\
    - Make the test work (GREEN) \\
    - Improve the code and eliminate duplication (REFACTOR)
  \end{flushleft}
  \textbf{Test Driven Development (TDD)}
}

\card{
  Give some reasons why you would use \textbf{Test Driven Development}?
}{
  \begin{flushleft}
    - Quality Assurance becomes proactive rather than reactive. \\ 
    - Estimations can be accurate enough to involve real customers in daily development. \\ 
    - Short iterations. Each iteration produces a working product. \\ 
    - Encourages good OO design practise. \\ 
    - Encourages design for testability. \\ 
    - Get an unambiguous progress meter. \\ 
    - Build up a set of regression test as we go along.
  \end{flushleft}
  Test Driven Development
}

\card{
  What are the limitations of TDD?
}{
  Conceptually hard to start with \\
  Can all programming tasks be driven by tests \\
    - Security \\
    - Concurrency \\
    - Performance
}

\flashcard{
  HTTP status codes:
  - 1xx: \blank{information} \\
  - 2xx: \blank{successful} \\
  - 3xx: \blank{redirection} \\
  - 4xx: \blank{client error}
}