
\card{
  What does saying that algorithm A runs in time g mean?
}{
  Given an input of size n, the number of operations executed by A is bounded above by g(n).
}

\card{
  What is a permutation of a set?
}{
  A 1-to-1 map of the set onto itself. In basic terms, it is a set mapped to
  another order of itself. i.e $[0,1,2,3,4] \mapsto [2,4,1,0,3]$
}

\card{
  What do we mean by a composition of two permutations?
}{
  The composition is the product of two permutations, $\alpha$ and $\beta$, on a set
  n, given by $\alpha \cdot \beta (n)$ or $\beta (\alpha(n))$
}

\card{
  What is the number of possible permutations on an n-element set?
}{
  $n!$
}

\card{
  In the context of a permutation, what do we mean by a transposition?
}{
  A transposition is a special kind of permutation where only 2 elements in
  a set are affected (they are swapped). On a set $X$ a transposition
  $\sigma = (i, j)$ is given by
  \[ \sigma(k) =
    \begin{cases}
      j  & \quad \text{if k = i}\\
      i  & \quad \text{if k = j}\\
      k  & \quad \text{ow.}
    \end{cases}
  \]
}

\card{
  Convert this pair of simultaneous equations into matrix form \\
  $a_{1,1} x_1 + a_{1,2} x_2 = b_1$\\
  $a_{2,1} x_2 + a_{2,2} x_2 = b_2$
}{
\[
 \begin{pmatrix}
  a_{1,1} & a_{1,2} \\
  a_{2,1} & a_{2,2}
 \end{pmatrix}
 \begin{pmatrix}
  x_{1} \\
  x_{2}
\end{pmatrix} =
\begin{pmatrix}
  b_{1} \\
  b_{2}
 \end{pmatrix}
\]
}

\card{
  What is the determinant of the matrix:
  \[  \begin{pmatrix}
      a_{1} & a_{2} \\
      a_{3} & a_{4}
    \end{pmatrix}
 \]
}{
  $a_1a_4 - a_2a_3$ \\
  Often denoted as:
  \[\begin{vmatrix}
      a_{1} & a_{2} \\
      a_{3} & a_{4}
    \end{vmatrix}
 \] \\
 The original system of equations to which the matrix corresponds only has
 a unique solution if the determinant is non-zero.
}

\card{
  What is an upper triangular matrix and how do you calculate its determinant?
}{
  It is a matrix where all of its entries below the diagonal are zero.
  \[
 \begin{pmatrix}
  a_{1,1} & a_{1,2} & \cdots & a_{1,n} \\
  0 & a_{2,2} & \cdots & a_{2,n} \\
  \vdots  & \vdots  & \ddots & \vdots  \\
  0 & 0 & \cdots & a_{n,n}
 \end{pmatrix}
 \]
 Its determinant is calculated by taking the product of the entries on the
 diagonal. i.e $a_{1,1} \cdot a_{2,2} \cdot ... \cdot a_{n,n}$
}

\card{
  Which 4 operations have no effect on a matrix's determinant?
}{
  Transposing two rows \\
  Transposing two columns \\
  Adding a multiple of one row to another \\
  Adding a multiple of one column to another \\
  Also note that if all entries in any row or column are 0 then the determinant
  is 0
}
