% Bascically just an adaption of Todd Davies flashcards for the subjects,
% with plans to basically expand upon them

\documentclass[frontgrid]{flacards}
\usepackage{color}
% For funky database symbols
\usepackage{newlfont}
\usepackage{tabularx}
\usepackage{graphicx}

\definecolor{light-gray}{gray}{0.75}
\fboxsep=20pt

\newcommand{\frontcard}[1]{\fboxsep=2pt\textcolor{light-gray}{\colorbox{light-gray}{$#1$}}}
\newcommand{\backcard}[1]{#1}
\newcommand\tab[1][0.5cm]{\hspace*{#1}}

\newcommand{\flashcard}[1]{% create new command for cards with blanks
    \card{% call the original \card command with twice the same argument (#1)
        \let\blank\frontcard% but let \blank behave like \frontcard the first time
        #1
    }{%
        \let\blank\backcard% and like \backcard the second time
        #1
    }%
}

\begin{document}

\pagesetup{2}{4} 

% Verilog Paul Nutter %

\flashcard{\blank{Abstraction}: hiding the complexity of the design.}

\flashcard{The \blank{datapath} realises the data operations required by the FSM.}

\flashcard{The \blank{control} issues signals to control the operation of the datapath.}

\card{
  A Reduced Instruction Set Computer (RISC) has three instruction types. What are they, and in brief what do they do? \textbf{Hint: Stump is a RISC computer}
}{
  Register to Register: Instructions that perform operations on values inside of registers.\\
  Load/Store: The only operations that will be on memory.\\
  Branch: Operations that change the value of the PC depending on a certain condition.
}

\flashcard{You use bit \blank{12} to determine whether an instruction is Type 1 or 2.}

\flashcard{Shifter operations are applied to the \blank{srcA} register in type \blank{1} operations.}

\card{
  In Verilog, there are four options for a bit to be. 0, 1, X and Z.\\In brief, what does each one mean?
}{
  1 and 0 are True and False respectively.\\A value of X is unknown logic. \\A value of Z would be high impedance.
}

\card{
  What type of circuits do you associate the use of\\
  i)  blocking statements, and\\
  ii) non-blocking statements\\
  in Verilog code?
}{
  Blocking statements use $=$, and are associated with combinatorial logic and execute one at a time.\\
  Non-blocking statements use $<=$, and are associated with sequential systems that use a clock and actions are executed concurrently. 
}

\card{
  Do you have to use the default case in Verilog? When would you use it?
}{
  Not necessarily. It is useful to cover cases not listed in the case statement, trapping any invalid states you shouldn't be in.
}

\card{
  What is the difference between a Verilog \textbf{task} and a Verilog \textbf{function}?
}{
  A task can change any number of outputs whereas a function can update only one.
}

\card{
  Where would you locate a \textbf{task} or \textbf{function} in your Verilog code?
}{
  It needs to be within the module but outside any always/initial blocks.
}

\card{
  Why does Stump's R0 exist? Give some examples illustrating its use.
}{
  Allows you to enable further operations to be implemented that are not part of the ISA.\\
  \begin{tabularx}{0.32\textwidth}{l X}
    - & MOV: ADD  R3, R2, R0\\
    - & NOP: ADD  R0, R0, R0\\
    - & CMP: SUBS R0, R3, R4\\
	\end{tabularx}
}

\card{
  What is a load/store architecture?
}{
  Data within registers will only be operated on, with results being written back to registers. LD/ST operations will be included for memory operations.
}

\card{
  How would you setup a Stump FSM with the inputs \textit{clk}, \textit{rst}, a 16 bit \textit{ir} and a 2 bit register for \textit{state}?
}{
  \begin{flushleft}
    module Stump\_FSM (input  wire	     clk,	\\
                  \tab\tab input  wire	     rst,	\\
                  \tab\tab input  wire [15:0] ir, \\
                  \tab\tab output reg  [ 1:0] state); \\    
    endmodule
  \end{flushleft}
  Stump FSM
}

\card{
  How would you design a \textbf{clock} for a verilog test?
}{
  \begin{flushleft}
    always \\
    \tab begin \\
    \tab\tab \#100 // Time per clock change \\
    \tab\tab clock = !clock \\ 
    \tab end
  \end{flushleft}
  Clock example
}

\card{
  How would you instantiate a Stump\_FSM with the inputs \textit{clk}, \textit{rst}, an \textit{ir} and a \textit{state} for testing?
}{
  \begin{flushleft}
    Stump\_FSM variableName ( \\
    \tab .clk(var1), .rst(var2), .ir(var3), .state(var4) \\
    );
  \end{flushleft}
  Instantiated Stump\_FSM
}

\card{
  In Stump, name the four \textbf{flags} and, when \textbf{'S'} is appended to an instruction, how they go high.
}{
  \begin{flushleft}
    \textbf{N} - the negative flag is set if the ALU result is negative. \\
    \textbf{Z} - the zero flag is set if the result is zero. \\
    \textbf{V} - the overflow is set if the result from an addition/subtraction interpreted as a two's complement is wrong. \\
    \textbf{C} - the carry flag is set if there is a carry out from the most significant bit of the result (bit 15).
  \end{flushleft}
  Flags
}

\flashcard{
  The \blank{Sign Extender} extends immediate values in Stump for Type 2 and Type 3 instructions.
}

\flashcard{
  The \blank{Shifter} in stump performs shift operations on the srcA register on Type 1 instructions.
}

% The rest Dirk Koch %

\card{
  What are the differences between the \textbf{Von Neuman} architecture and the \textbf{Harvard} architecture?
}{
  \begin{flushleft}
    \textbf{Von Neuman} \\
    - has one bus for both data transfers and instructions fetches. \\
    - a single, unified cache, which stores both instructions and data. \\
    \textbf{Harvard} \\
    - has separate data and instruction busses, allowing transfers to be performed simultaneously on both busses. \\
    - separate caches for each bus, as a shared cache would be difficult to manage.
  \end{flushleft}
  \textbf{Von Neuman} v.s. \textbf{Harvard}
}

\card{
  Compare and contrast the \textbf{ARM} ISA's and the \textbf{x86} ISA's techniques for branching to a subroutine.
}{
  \begin{flushleft}
    \textbf{ARM} \\
    - Single register allows for less implementation cost. \\
    - Any other branch call will overwrite value in link register. \\
    \textbf{x86} \\
    - Stack based system has greater implementation cost. \\
    - Allows for branch calls within branches, without loss of address.
  \end{flushleft}
  ARM ISA vs x86 ISA
}

\flashcard{
  \blank{Instruction Set Architecture} (ISA) is the visible view of the processor (what is exposed to the programmer).
}

\flashcard{
  \blank{Microarchitecture} is the hardware view on a processor. 
}

\card{
  Name some ways that a processor can be made faster.
}{
  \begin{flushleft}
    \textbf{Increase the clock rate} \\
    - As a consequence of Moore's Law \\
    - Through circuit design \\
    - Through microarchitectural design, e.g. more parallelism \\
    \textbf{Do more in each cycle} \\
    - Parallelism within instruction execution \\
    \textbf{Do more in each instruction} \\
    - Somewhat limited by ISA as a completely new ISA is expensive.
  \end{flushleft}
  Some possible ways of making a processor faster
}

\card{
  What are the basic principles of \textbf{pipelining}?
}{
  Pipelining works by starting executing one instruction before its predecessor(s) have finished. The time taken for a circuit to evaluate is a bit uncertain, so instructions are deliberately separated into \textbf{stages} with pipeline \textbf{latches}.
}

\flashcard{
  \blank{Latches} prevent one operation from overrunning its predecessor (by delaying it).
}

\card{
  How does pipelining effect latency?
}{
  It increases latency, with the speed being limited by the slowest stage.
}

\card{
  What is the potential speed up of pipelining? Why isn't this always the case?
}{
  Partitioning a task into N stages gives a maximum speed-up of N times. \\
  This assumes that all stages take exactly the same time and that the partitioning has some added cost due to the delay imposed by the pipeline registers.
}

\flashcard{
  A \blank{Digital Signal Processor} (DSP) is specialised for high performance in a particular subset of computing tasks.
}

\card{
  What is saturating arithmetic?
}{
  In two's complement arithmetic, adding two large positive numbers may result in an overflow. A Digital Signal Processor (DSP) may sometimes find it better to "clip" the value to the maximum representable one. This is called "saturation".
}

\flashcard{\blank{Single instruction, multiple data} (SIMD) describes computers with multiple processing elements that perform the same operation on multiple data points simultaneously.}

\card{
  What are the two basic types of \textbf{MOS-FETs} (Metal-Oxide-Semiconductor Field Effect Transistors)?
}{
  \begin{flushleft}
    \textbf{NMOS} - with n-type channel (analogy to normally open switch) \\
    \textbf{PMOS} - with p-type channel (analogy to normally closed switch)
  \end{flushleft}
  Two types of MOS-FETs
}

\card{
  How do you calculate system performance?
}{
  $time per task = clock period \times number of clock cycles per task$ \\
  $performance \approx 1 / (time per task)$
}

\card{
  When changing a functional design into a physical one, what is on the "wish list" of properties?
}{
  \begin{flushleft}
    - Clock period (performance) \\
    - Floorplan/pinout \\
    - Area/density (cost) \\
    \tab Using all the chip area for useful gates, but keeping the chip small to save cost. \\
    - Power
  \end{flushleft}
  Wish list of properties
}

\card{
  What does \textbf{PVT} stand for in the context of chip design?
}{
  \begin{flushleft}
    - Manufacturing \textbf{P}rocess variation \\
    - Varying operating \textbf{V}oltage \\
    \tab Typical voltage ranges my be $\pm 10\%$ \\
    - Different chip \textbf{T}emperature
  \end{flushleft}
  Typically, run simulation at extremes
}

\end{document} 
